---
title: "crab_size_shoot_density"
author: "Rebecca Cates"
date: "6/11/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Load libraries
```{r warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
```

#Read in crab and shoot density data
```{r}
crab <- read.csv("clean_crab_otter_size_data_all_years.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) #eventually source from KNB

shoot <- read.csv("shoot_density.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) #eventually source from KNB

bio <- read.csv("seagrass_biomass.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) #eventually source from KNB
```

#Clean up "shoot" df, calculate m2 shoot-density, and join with size data
```{r}
#clean up shoot df
shoot <-
  shoot %>% 
  rename(year = ï..year) %>% 
  mutate(eg_shoot_msq = shoot_dens*4)

#Clean up sg biomass df
bio <-
  bio %>% 
  dplyr::select(-c("X", "site_2019", "bay_code", "X.1", "X.2", "X.3"))

#Join data
crab <- left_join(crab, shoot, by= "sec_key")
crab <- left_join(crab, bio, by= "sec_key")

crab <-
  crab %>% 
  dplyr::select(-c("bay_code.y", "bay_code.x", "sex", "shoot_dens", "shoot_dens_se")) %>% 
  rename(eg_mass_msq = avg_biom_msq)
```

#Fill in year column
```{r}
crab$year<- NA
crab$year[1:120] <- 2020
crab$year[121:381] <- 2017
crab$year[382:490] <- 2018
crab$year[491:754] <- 2019
```

#Remove NAs from where there is no shoot density data
```{r}
crab <- crab[!is.na(crab$eg_mass_msq), ]
crab <- crab[!is.na(crab$eg_shoot_msq), ]
```

#Filter for species 
```{r}
crab_dun <-
  crab %>% 
  filter(SpCode %in% c("CRABDUN"))

crab_gra <-
  crab %>% 
  filter(SpCode %in% c("CRABGRA"))

crab_red <-
  crab %>% 
  filter(SpCode %in% c("CRABRR"))

crab_hel <-
  crab %>% 
  filter(SpCode %in% c("CRABHEL"))
```

#Filter for correct years for C. magister and M. gracilis
```{r}
crab_dun <-
  crab_dun %>% 
  filter(year %in% c("2019", "2020"))

crab_gra <-
  crab_gra %>% 
  filter(year %in% c("2019", "2020"))
```


#Data visualization with untransformed data, size ~ sg shoot
```{r}

ggplot(data = crab_hel, aes(x = otter_density, y= carapace_width_mm))+
  geom_point(size = 3) +
  theme_classic()+
  labs(x=expression(Sea~otter~density~(ind.~km^-2)), y= "Crab carapace width (mm)")+
   theme(text = element_text(size=20))+
  xlim(0,27)

expression(Shoot~density~(no.~m^-2))
expression(Seagrass~biomass~(g.~m^-2))
expression(Sea~otter~density~(ind.~km^-2))

#C. magister==================================================
d.size <- ggplot(data = crab_dun, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
 geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression("A)"))+
   theme(text = element_text(size=20), axis.title = element_blank())
#M. gracilis =====================================================
g.size <- ggplot(data = crab_gra, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"B)"))+
    theme(text = element_text(size=20), axis.title = element_blank())
#C. productus=====================================================
r.size <- ggplot(data = crab_red, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"C)"))+
    theme(text = element_text(size=20), axis.title = element_blank())
#T. cheiragonus======================================================
h.size <- ggplot(data = crab_hel, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"D)"))+
   theme(text = element_text(size=20), axis.title = element_blank())

d.size
g.size
r.size
h.size
#arrange all plots 
size.shoot <- gridExtra::grid.arrange(d.size, g.size, r.size, h.size,  ncol=1, nrow = 4)

annotate_figure(size.shoot, bottom = text_grob(expression(Shoot~density~(no.~m^-2)), size = 20),left = text_grob("Carapace width (mm)", rot=90, size = 20))
```

#Data visualization with sqrt data, size~ sg shoot
```{r}
#C. magister==================================================
ggplot(data = crab_dun, aes(x = sqrt(eg_shoot_msq), y= sqrt(carapace_width_mm)))+
  geom_point() +
 geom_smooth(method = "gaussian", formula = y~x)+
  labs(x= "Shoot Density", y= "Carapace Width (mm)", title=expression(paste(italic("C. magister"))))+
  theme(text = element_text(size=15))
#M. gracilis =====================================================
ggplot(data = crab_gra, aes(x = sqrt(eg_shoot_msq), y= sqrt(carapace_width_mm)))+
  geom_point() +
  geom_smooth(method = "gaussian", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("M. gracilis"))))+
  theme(text = element_text(size=15))
#C. productus=====================================================
ggplot(data = crab_red, aes(x = sqrt(eg_shoot_msq), y= sqrt(carapace_width_mm)))+
  geom_point() +
  geom_smooth(method = "gaussian", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("C. productus"))))+
  theme(text = element_text(size=15))
#T. cheiragonus======================================================
ggplot(data = crab_hel, aes(x = sqrt(eg_shoot_msq), y= sqrt(carapace_width_mm)))+
  geom_point() +
  geom_smooth(method = "gaussian", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("T. cheiragonus"))))+
  theme(text = element_text(size=15))
```

#Data visualization with untransformed data, size~ sg biomass
```{r}
#C. magister==================================================
d.size <- ggplot(data = crab_dun, aes(x = eg_mass_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
 geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Carapace width (mm)", title=expression("A)"))+
   theme(text = element_text(size=15), axis.title = element_blank())
#M. gracilis =====================================================
g.size <- ggplot(data = crab_gra, aes(x = eg_mass_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Carapace width (mm)", title=expression("B)"))+
    theme(text = element_text(size=15), axis.title = element_blank())
#C. productus=====================================================
r.size <- ggplot(data = crab_red, aes(x = eg_mass_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Carapace width (mm)", title=expression("C)"))+
    theme(text = element_text(size=15), axis.title = element_blank())
#T. cheiragonus======================================================
h.size <- ggplot(data = crab_hel, aes(x = eg_mass_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Carapace width (mm)", title=expression("D)"))+
   theme(text = element_text(size=15), axis.title = element_blank())

d.size
g.size
r.size
h.size

#arrange all plots 
size <- gridExtra::grid.arrange(d.size, g.size, r.size, h.size,  ncol=1, nrow = 4)

annotate_figure(size, bottom = text_grob(expression(Seagrass~biomass~(g.~m^-2)), size = 20),left = text_grob("Carapace width (mm)", rot=90, size = 20))
```

#Data analysis
#C. magister
```{r}
#Run GLMs
dun1 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq + eg_mass_msq, data = crab_dun, family = gaussian(link = "log"))
summary(dun1)

dun2 <- glm(carapace_width_mm ~ otter_density  + eg_mass_msq, data = crab_dun, family = gaussian(link = "log"))
summary(dun2)

dun3 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun3)

dun4 <- glm(carapace_width_mm ~ eg_shoot_msq + eg_mass_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun4)

dun5 <- glm(carapace_width_mm ~ otter_density, data = crab_dun, family = gaussian(link = "log"))
summary(dun5)

dun6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_dun, family = gaussian(link = "log"))
summary(dun6)

dun7 <- glm(carapace_width_mm ~ eg_mass_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun7)

dun8 <- glm(carapace_width_mm ~ otter_density*eg_shoot_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun8)

dun9 <- glm(carapace_width_mm ~ otter_density*eg_mass_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun9)

dun10 <- glm(carapace_width_mm ~ eg_shoot_msq*eg_mass_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun10)

#Create list of models
dun_models <- list(dun1,dun2,dun3,dun4,dun5,dun6,dun7,dun8,dun9)
names(dun_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(dun1);AICc(dun2);AICc(dun3);AICc(dun4);AICc(dun5);AICc(dun6);AICc(dun7);AICc(dun8);AICc(dun9)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(dun_models, modnames = names(dun_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#M. gracilis
```{r}
#Run GLMs
gra1 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq + eg_mass_msq, data = crab_gra, family = gaussian(link = "log"))
summary(gra1)

gra2 <- glm(carapace_width_mm ~ otter_density  + eg_mass_msq, data = crab_gra, family = gaussian(link = "log"))
summary(gra2)

gra3 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra3)

gra4 <- glm(carapace_width_mm ~ eg_shoot_msq + eg_mass_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra4)

gra5 <- glm(carapace_width_mm ~ otter_density, data = crab_gra, family = gaussian(link = "log"))
summary(gra5)

gra6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_gra, family = gaussian(link = "log"))
summary(gra6)

gra7 <- glm(carapace_width_mm ~ eg_mass_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra7)

gra8 <- glm(carapace_width_mm ~ otter_density*eg_shoot_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra8)

gra9 <- glm(carapace_width_mm ~ otter_density*eg_mass_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra9)

gra10 <- glm(carapace_width_mm ~ eg_shoot_msq*eg_mass_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra10)

#Create list of models
gra_models <- list(gra1,gra2,gra3,gra4,gra5,gra6,gra7,gra8,gra9)
names(gra_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass")
#Calculate AICc
library(MuMIn)
AICc(gra1);AICc(gra2);AICc(gra3);AICc(gra4);AICc(gra5);AICc(gra6);AICc(gra7);AICc(gra8);AICc(gra9)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(gra_models, modnames = names(gra_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#C. productus
```{r}
#Run GLMs
red1 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq + eg_mass_msq, data = crab_red, family = gaussian(link = "log"))
summary(red1)

red2 <- glm(carapace_width_mm ~ otter_density  + eg_mass_msq, data = crab_red, family = gaussian(link = "log"))
summary(red2)

red3 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red3)

red4 <- glm(carapace_width_mm ~ eg_shoot_msq + eg_mass_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red4)

red5 <- glm(carapace_width_mm ~ otter_density, data = crab_red, family = gaussian(link = "log"))
summary(red5)

red6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_red, family = gaussian(link = "log"))
summary(red6)

red7 <- glm(carapace_width_mm ~ eg_mass_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red7)

red8 <- glm(carapace_width_mm ~ otter_density*eg_shoot_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red8)

red9 <- glm(carapace_width_mm ~ otter_density*eg_mass_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red9)

red10 <- glm(carapace_width_mm ~ (eg_shoot_msq)*eg_mass_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red10)

red10 <- glm(carapace_width_mm ~ otter_density*eg_mass_msq + eg_shoot_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red10)

#Create list of models
red_models <- list(red1,red2,red3,red4,red5,red6,red7,red8,red9)
names(red_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass")
#Calculate AICc
library(MuMIn)
AICc(red1);AICc(red2);AICc(red3);AICc(red4);AICc(red5);AICc(red6);AICc(red7);AICc(red8);AICc(red9)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(red_models, modnames = names(red_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#T. cheiragonus
```{r}
#Run GLMs
hel1 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq + eg_mass_msq, data = crab_hel, family = gaussian(link = "log"))
summary(hel1)

hel2 <- glm(carapace_width_mm ~ otter_density  + eg_mass_msq, data = crab_hel, family = gaussian(link = "log"))
summary(hel2)

hel3 <- glm(carapace_width_mm ~ otter_density + eg_shoot_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel3)

hel4 <- glm(carapace_width_mm ~ eg_shoot_msq + eg_mass_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel4)

hel5 <- glm(carapace_width_mm ~ otter_density, data = crab_hel, family = gaussian(link = "log"))
summary(hel5)

hel6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_hel, family = gaussian(link = "log"))
summary(hel6)

hel7 <- glm(carapace_width_mm ~ eg_mass_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel7)

hel8 <- glm(carapace_width_mm ~ otter_density*eg_shoot_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel8)

hel9 <- glm(carapace_width_mm ~ otter_density*eg_mass_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel9)

hel10 <- glm(carapace_width_mm ~ eg_shoot_msq*eg_mass_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel10)

#Create list of models
hel_models <- list(hel1,hel2,hel3,hel4,hel5,hel6,hel7,hel8,hel9)
names(hel_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass")
#Calculate AICc
library(MuMIn)
AICc(hel1);AICc(hel2);AICc(hel3);AICc(hel4);AICc(hel5);AICc(hel6);AICc(hel7);AICc(hel8);AICc(hel9)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(hel_models, modnames = names(hel_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#Visreg plots for all species and predictor variables
```{r}
#visreg dung
fig.dun1 <- visreg(dun9, "otter_density", band= TRUE, scale = "response", gg = TRUE, rug=FALSE)+
   geom_point(data = crab_dun, aes(otter_density, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Sea~otter~density~(ind.~km^-2)), y= "Crab size", title=expression("A)"))+
 theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)+
  xlim(0,30)
 
fig.dun2 <- visreg(dun9, "eg_mass_msq", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
  geom_point(data = crab_dun, aes(eg_mass_msq, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Crab size", title=expression("B)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)+
  xlim(0,250)
#visreg slender
fig.gra1 <- visreg(gra9, "otter_density", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   geom_point(data = crab_gra, aes(otter_density, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Sea~otter~density~(ind.~km^-2)), y= "Crab size", title=expression("C)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)+
  xlim(0,30)

fig.gra2 <- visreg(gra9, "eg_mass_msq", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   geom_point(data = crab_gra, aes(eg_mass_msq, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Crab abundance", title=expression("D)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)+
  xlim(0,250)

#visreg red rock
fig.red1 <- visreg(red10, "otter_density", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
  geom_point(data = crab_red, aes(otter_density, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Sea~otter~density~(ind.~km^-2)), y= "Crab size", title=expression("E)"))+
 theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)+
  xlim(0,30)
 
fig.red2 <- visreg(red10, "eg_mass_msq", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
  geom_point(data = crab_red, aes(eg_mass_msq, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Crab size", title=expression("F)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)+
  xlim(0,250)
 
fig.red3 <- visreg(red10, "eg_shoot_msq", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   geom_point(data = crab_red, aes(eg_shoot_msq, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab size", title=expression("G)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank(), axis.title.x = element_blank())+
  ylim(0,200)

#visreg helmet
fig.hel1 <- visreg(hel8, "otter_density", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   geom_point(data = crab_hel, aes(otter_density, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Sea~otter~density~(ind.~km^-2)), y= "Crab size", title=expression("H)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank())+
  ylim(0,200)+
  xlim(0,30)
 
fig.hel2 <- visreg(hel8, "eg_shoot_msq", band= TRUE, scale="response", gg = TRUE,rug=FALSE)+
   geom_point(data = crab_hel, aes(eg_shoot_msq, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab size", title=expression("I)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank())+
  ylim(0,200)

fake.fig <- visreg(red10, "eg_shoot_msq", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   geom_point(data = crab_hel, aes(eg_shoot_msq, carapace_width_mm))+
   theme_classic()+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Crab size", title=expression("F)"))+
  theme(text = element_text(size=20), axis.title.y = element_blank())+
  ylim(0,200)


```

#arrange visreg plots
```{r}
vis.dun <- gridExtra::grid.arrange(fig.dun1, fig.dun2, ncol=3, nrow = 1)
vis.gra <- gridExtra::grid.arrange(fig.gra1,fig.gra2, ncol=3, nrow = 1)
vis.red <- gridExtra::grid.arrange(fig.red1,fig.red2,fig.red3, ncol=3, nrow = 1)
vis.hel <- gridExtra::grid.arrange(fig.hel1, fake.fig,fig.hel2, ncol=3, nrow = 1)

vis.all <- gridExtra::grid.arrange(vis.dun, vis.gra, vis.red, vis.hel, ncol=1, nrow = 4)

vis.all1 <- annotate_figure(vis.all, left = text_grob("Crab carapace width (mm)", rot=90, size = 20))
vis.all1
```


#Calculate percent change for tble values
```{r}
exp(-6.254*10^-5)


100*(exp(8-6.254*10^-5)-1)
```

#rename columns for clarity in correlation plots
```{r}
names(crab_dun) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')

names(crab_gra) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')

names(crab_red) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')

names(crab_hel) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')
```


#Corrgram for independent variables
```{r}
#correlations
corrgram(crab_dun[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")

#correlations
corrgram(crab_gra[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")

#correlations
corrgram(crab_red[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")

#correlations
corrgram(crab_hel[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")
```

#VIF correlation check 
```{r}
dun1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_dun)
car::vif(dun1)

gra1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_gra)
car::vif(gra1)

red1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_red)
car::vif(red1)

hel1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_hel)
car::vif(hel1)
```
