---
title: "crab_size_shoot_density"
author: "Rebecca Cates"
date: "6/11/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
This script is associated with the manuscript "Effect of Sea Otter (Enhydra lutris) Predation and Habitat Structure on Nearshore Crab Assemblages in Southeast Alaska" by Rebecca Cates, Wendel Raymond, Lia Domke, and Ginny Eckert. This manuscript has been adapted from R.Cates master's thesis at the University of Alaska Fairbanks College of Fisheries and Ocean Science and is associated with the large, interdisciplinary project "APECS".

Crab size distribution data were collected along the western coastline of Prince of Wales island with sites ranging 93 km from the most southern site in Dunbar Inlet up to the most northern site in Naukati Bay. Data was collected July to August, 2017-2020. Four strings with 2 pots each were were set at 21 different eelgrass sites. Pots soaked for ~24 hours before being pulled up to identify, measure and sex the contents of the pot.

In addition, sea otter density data and shoot density data were collected at these same sites from July through August, 2017-2020. Sea otters were counted via boat based surveys 2 nautical miles around the eelgrass sites. Multiple individuals with binoculars were stationed at all angles from a 22' dual engine North River as the boat proceeded at a max speed of 8 knots. Sea otters were noted on the app "INAVX" with waypoints. Density per site was calculated in the script "Sea_otter_impact_index". Seagrass shoot density data was collected in 2017, 2018, and 2020 with eight 0.5-m × 0.5-m quadrats were evenly spaced every 12 m along a 100-m transect placed approximately -0.5 m relative to MLLW (Raymond et al. 2021). Eelgrass shoots were counted in each quadrat. Shoot density was then averaged across the eight quadrats per site. At each site in 2019, five 0.5-m x 0.5-m quadrats were randomly placed roughly 5-m linear distance below the upper edge of the eelgrass bed at all sites. Eelgrass shoots were counted in each quadrat and averaged.


Goal of this script :
1) Check for errors in data
2) Check for accuracy of data type and fix if needed (e.g., factor, numeric, character)
3) Analyze crab size data for all species
4) Visualize data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Load libraries
```{r warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(visreg)
library(tidyverse)
library(gridExtra)
library(ggthemes)
library(quotidieR)
```

#Read in crab, otter, and shoot density data
```{r}
crab <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/Crab_Size_Seagrass/crabsize_otterdensity_data.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) 

shoot <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/Crab_Size_Seagrass/shoot_density.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))
```

#Clean up "shoot" df, calculate m2 shoot-density, calculate sea otter presence, and join with size data
```{r}
#calculate shoot per meter squared
shoot <-
  shoot %>% 
  mutate(eg_shoot_msq = shoot_dens*4)

#Join data
crab <- left_join(crab, shoot, by= "sec_key")

#clean up and make year a factor
crab <-
  crab %>% 
  dplyr::select(-c("bay_code.y", "bay_code.x", "sex", "shoot_dens", "shoot_dens_se"))

#Sea otter presence
crab <- crab %>% 
  mutate(otter_presence = if_else(otter_density == 0, "Absent", 'Present'))

crab$year <- as.factor(crab$year)
crab$otter_presence <- as.factor(crab$otter_presence)
str(crab)
```

#Remove NAs from where there is no shoot density data
```{r}
crab <- crab[!is.na(crab$eg_shoot_msq), ]
```

#Filter for species 
```{r}
crab_dun <-
  crab %>% 
  filter(SpCode %in% c("CRABDUN"))

crab_gra <-
  crab %>% 
  filter(SpCode %in% c("CRABGRA"))

crab_red <-
  crab %>% 
  filter(SpCode %in% c("CRABRR"))

crab_hel <-
  crab %>% 
  filter(SpCode %in% c("CRABHEL"))

```

#Filter years for C. magister and M. gracilis, MUTED
```{r}
crab_dun <-
 crab_dun %>% 
  filter(year %in% c("2019", "2020"))

crab_gra <-
  crab_gra %>% 
  filter(year %in% c("2019", "2020"))
```

#Data visualization with untransformed data, size ~ sg shoot
```{r}
#Figure axis titles to copy and paste:
#expression(Shoot~density~(no.~m^-2))
#expression(Seagrass~biomass~(g.~m^-2))
#expression(Sea~otter~density~(ind.~km^-2))

#C. magister==================================================
d.size <- ggplot(data = crab_dun, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
 geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression("A)"))+
   theme(text = element_text(size=20), axis.title = element_blank())
#M. gracilis =====================================================
g.size <- ggplot(data = crab_gra, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"B)"))+
    theme(text = element_text(size=20), axis.title = element_blank())
#C. productus=====================================================
r.size <- ggplot(data = crab_red, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"C)"))+
    theme(text = element_text(size=20), axis.title = element_blank())

ggplot(data = crab_red, aes(x = otter_presence, y= carapace_width_mm))+
  geom_boxplot() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"C)"))+
    theme(text = element_text(size=20), axis.title = element_blank())
#T. cheiragonus======================================================
h.size <- ggplot(data = crab_hel, aes(x = eg_shoot_msq, y= carapace_width_mm))+
  geom_point() +
  theme_classic()+
  geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  #labs(x=expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(~"D)"))+
   theme(text = element_text(size=20), axis.title = element_blank())

d.size
g.size
r.size
h.size

#arrange all plots 
size.shoot <- gridExtra::grid.arrange(d.size, g.size, r.size, h.size,  ncol=1, nrow = 4)

annotate_figure(size.shoot, bottom = text_grob(expression(Shoot~density~(no.~m^-2)), size = 20),left = text_grob("Carapace width (mm)", rot=90, size = 20))
```

#Data analysis
#C. magister
```{r}
#Run GLMs
dun1 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq + year, data = crab_dun, family = gaussian(link = "log"))
summary(dun1)

dun2 <- glm(carapace_width_mm ~ otter_presence  + year, data = crab_dun, family = gaussian(link = "log"))
summary(dun2)

dun3 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun3)

dun4 <- glm(carapace_width_mm ~ eg_shoot_msq + year, data = crab_dun,  family = gaussian(link = "log"))
summary(dun4)

dun5 <- glm(carapace_width_mm ~ otter_presence, data = crab_dun, family = gaussian(link = "log"))
summary(dun5)

dun6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_dun, family = gaussian(link = "log"))
summary(dun6)

dun7 <- glm(carapace_width_mm ~ year, data = crab_dun,  family = gaussian(link = "log"))
summary(dun7)

dun8 <- glm(carapace_width_mm ~ otter_presence*eg_shoot_msq, data = crab_dun,  family = gaussian(link = "log"))
summary(dun8)

dun9 <- glm(carapace_width_mm ~ otter_presence*year, data = crab_dun,  family = gaussian(link = "log"))
summary(dun9)

dun10 <- glm(carapace_width_mm ~ eg_shoot_msq*year, data = crab_dun,  family = gaussian(link = "log"))
summary(dun10)

#Create list of models
dun_models <- list(dun1,dun2,dun3,dun4,dun5,dun6,dun7,dun8,dun9,dun10)
names(dun_models) <- c("~sea otter presence + shoot density + year", "~sea otter_presence + year", "~sea otter presence + shoot density", "~shoot density + year", "~sea otter presence", "~shoot density", "~year", "~sea otter presence*shoot density", "~sea otter presence*year", "~shoot density*year" )
#Calculate AICc
library(MuMIn)
AICc(dun1);AICc(dun2);AICc(dun3);AICc(dun4);AICc(dun5);AICc(dun6);AICc(dun7);AICc(dun8);AICc(dun9);AICc(dun10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(dun_models, modnames = names(dun_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#M. gracilis
```{r}
#Run GLMs
gra1 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq + year, data = crab_gra, family = gaussian(link = "log"))
summary(gra1)

gra2 <- glm(carapace_width_mm ~ otter_presence  + year, data = crab_gra, family = gaussian(link = "log"))
summary(gra2)

gra3 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra3)

gra4 <- glm(carapace_width_mm ~ eg_shoot_msq + year, data = crab_gra,  family = gaussian(link = "log"))
summary(gra4)

gra5 <- glm(carapace_width_mm ~ otter_presence, data = crab_gra, family = gaussian(link = "log"))
summary(gra5)

gra6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_gra, family = gaussian(link = "log"))
summary(gra6)

gra7 <- glm(carapace_width_mm ~ year, data = crab_gra,  family = gaussian(link = "log"))
summary(gra7)

gra8 <- glm(carapace_width_mm ~ otter_presence*eg_shoot_msq, data = crab_gra,  family = gaussian(link = "log"))
summary(gra8)

gra9 <- glm(carapace_width_mm ~ otter_presence*year, data = crab_gra,  family = gaussian(link = "log"))
summary(gra9)

gra10 <- glm(carapace_width_mm ~ eg_shoot_msq*year, data = crab_gra,  family = gaussian(link = "log"))
summary(gra10)

#Create list of models
gra_models <- list(gra1,gra2,gra3,gra4,gra5,gra6,gra7,gra8,gra9,gra10)
names(gra_models) <- c("~sea otter presence + shoot density + year", "~sea otter_presence + year", "~sea otter presence + shoot density", "~shoot density + year", "~sea otter presence", "~shoot density", "~year", "~sea otter presence*shoot density", "~sea otter presence*year", "~shoot density*year" )
#Calculate AICc
library(MuMIn)
AICc(gra1);AICc(gra2);AICc(gra3);AICc(gra4);AICc(gra5);AICc(gra6);AICc(gra7);AICc(gra8);AICc(gra9);AICc(gra10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(gra_models, modnames = names(gra_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#C. productus
```{r}
#Run GLMs
red1 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq + year, data = crab_red, family = gaussian(link = "log"))
summary(red1)

red2 <- glm(carapace_width_mm ~ otter_presence  + year, data = crab_red, family = gaussian(link = "log"))
summary(red2)

red3 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red3)

red4 <- glm(carapace_width_mm ~ eg_shoot_msq + year, data = crab_red,  family = gaussian(link = "log"))
summary(red4)

red5 <- glm(carapace_width_mm ~ otter_presence, data = crab_red, family = gaussian(link = "log"))
summary(red5)

red6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_red, family = gaussian(link = "log"))
summary(red6)

red7 <- glm(carapace_width_mm ~ year, data = crab_red,  family = gaussian(link = "log"))
summary(red7)

red8 <- glm(carapace_width_mm ~ otter_presence*eg_shoot_msq, data = crab_red,  family = gaussian(link = "log"))
summary(red8)

red9 <- glm(carapace_width_mm ~ otter_presence*year, data = crab_red,  family = gaussian(link = "log"))
summary(red9)

red10 <- glm(carapace_width_mm ~ eg_shoot_msq*year, data = crab_red,  family = gaussian(link = "log"))
summary(red10)

#Create list of models
red_models <- list(red1,red2,red3,red4,red5,red6,red7,red8,red9,red10)
names(red_models) <- c("~sea otter presence + shoot density + year", "~sea otter_presence + year", "~sea otter presence + shoot density", "~shoot density + year", "~sea otter presence", "~shoot density", "~year", "~sea otter presence*shoot density", "~sea otter presence*year", "~shoot density*year" )
#Calculate AICc
library(MuMIn)
AICc(red1);AICc(red2);AICc(red3);AICc(red4);AICc(red5);AICc(red6);AICc(red7);AICc(red8);AICc(red9);AICc(red10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(red_models, modnames = names(red_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#T. cheiragonus
```{r}
#Run GLMs
hel1 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq + year, data = crab_hel, family = gaussian(link = "log"))
summary(hel1)

hel2 <- glm(carapace_width_mm ~ otter_presence  + year, data = crab_hel, family = gaussian(link = "log"))
summary(hel2)

hel3 <- glm(carapace_width_mm ~ otter_presence + eg_shoot_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel3)

hel4 <- glm(carapace_width_mm ~ eg_shoot_msq + year, data = crab_hel,  family = gaussian(link = "log"))
summary(hel4)

hel5 <- glm(carapace_width_mm ~ otter_presence, data = crab_hel, family = gaussian(link = "log"))
summary(hel5)

hel6 <- glm(carapace_width_mm ~ eg_shoot_msq, data = crab_hel, family = gaussian(link = "log"))
summary(hel6)

hel7 <- glm(carapace_width_mm ~ year, data = crab_hel,  family = gaussian(link = "log"))
summary(hel7)

hel8 <- glm(carapace_width_mm ~ otter_presence*eg_shoot_msq, data = crab_hel,  family = gaussian(link = "log"))
summary(hel8)

hel9 <- glm(carapace_width_mm ~ otter_presence*year, data = crab_hel,  family = gaussian(link = "log"))
summary(hel9)

hel10 <- glm(carapace_width_mm ~ eg_shoot_msq*year, data = crab_hel,  family = gaussian(link = "log"))
summary(hel10)

#Create list of models
hel_models <- list(hel1,hel2,hel3,hel4,hel5,hel6,hel7,hel8,hel9,hel10)
names(hel_models) <- c("~sea otter presence + shoot density + year", "~sea otter_presence + year", "~sea otter presence + shoot density", "~shoot density + year", "~sea otter presence", "~shoot density", "~year", "~sea otter presence*shoot density", "~sea otter presence*year", "~shoot density*year" )
#Calculate AICc
library(MuMIn)
AICc(hel1);AICc(hel2);AICc(hel3);AICc(hel4);AICc(hel5);AICc(hel6);AICc(hel7);AICc(hel8);AICc(hel9);AICc(hel10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(hel_models, modnames = names(hel_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#Plots for all species and predictor variables
```{r}
#Figures for C. magister
# model 9 : size ~ otter presence

#1 visreg otter presence
visreg(dun5, "otter_presence", gg = TRUE, band= TRUE, scale = "response", rug=FALSE)+
  labs(x= expression(Sea~otter~presence), y= "Carapace width (mm)", title=expression(italic("C. magister")))+
  theme_Publication()

#ggplot otter presence
ggplot(data = crab_dun)+
  geom_boxplot(aes(x = otter_presence, y = carapace_width_mm), show.legend = FALSE)+
  labs(x= expression(Sea~otter~presence), y= "Carapace width (mm)", title=expression(italic("C. magister")))+
  theme_Publication()

#Figure for C. gracilis
#model 1 : size ~ otter + shoot density + year
#1 otter presence, can I add points to this?
visreg(gra1, "otter_presence", partial = FALSE, band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   labs(x= expression(Sea~otter~presence), y= "Carapace width (mm)", title=expression(italic("C. gracilis")))+
  theme_Publication()

#2 shoot density
visreg(gra1, "eg_shoot_msq", band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   geom_jitter(data = crab_gra, aes(eg_shoot_msq, carapace_width_mm))+
   theme_Publication()+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Carapace width (mm)", title=expression(italic("C. gracilis")))

#3 year
visreg(gra1, "year", partial = FALSE, band= TRUE, scale="response", gg = TRUE, rug=FALSE)+
   labs(x= expression(Year), y= "Carapace width (mm)", title=expression(italic("C. gracilis")))+
  theme_Publication()

#figure for C. productus
visreg(red9, "otter_presence", by="year", band= TRUE, scale = "response", gg = TRUE, rug=FALSE)

ggplot(data = crab_red)+
  geom_boxplot(aes(x = otter_presence, y = carapace_width_mm, fill = year), show.legend = FALSE)+
  labs(x= expression(Sea~otter~presence), y= "Carapace width (mm)", title=expression(italic("C. productus")))+
  facet_grid(. ~ year)+
  scale_fill_viridis_d()+
  theme_Publication()

#figure for T. cheiragonus
visreg(hel9, "otter_presence", by="year", band= TRUE, scale = "response", gg = TRUE, rug=FALSE)

ggplot(data = crab_hel)+
  geom_boxplot(aes(x = otter_presence, y = carapace_width_mm, fill = year), show.legend = FALSE)+
  labs(x= expression(Sea~otter~presence), y= "Carapace width (mm)", title=expression(italic("T. cheiragonus")))+
  facet_grid(. ~ year)+
  scale_fill_viridis_d()+
  theme_Publication()

```

#arrange visreg plots
```{r}
vis.dun <- gridExtra::grid.arrange(fig.dun1, fig.dun2, ncol=3, nrow = 1)
vis.gra <- gridExtra::grid.arrange(fig.gra1,fig.gra2, ncol=3, nrow = 1)
vis.red <- gridExtra::grid.arrange(fig.red1,fig.red2,fig.red3, ncol=3, nrow = 1)
vis.hel <- gridExtra::grid.arrange(fig.hel1, fake.fig,fig.hel2, ncol=3, nrow = 1)

vis.all <- gridExtra::grid.arrange(vis.dun, vis.gra, vis.red, vis.hel, ncol=1, nrow = 4)

vis.all1 <- annotate_figure(vis.all, left = text_grob("Crab carapace width (mm)", rot=90, size = 20))
vis.all1
```


#Calculate percent change for tble values
```{r}
exp(-6.254*10^-5)


100*(exp(8-6.254*10^-5)-1)
```

#rename columns for clarity in correlation plots
```{r}
names(crab_dun) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')

names(crab_gra) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')

names(crab_red) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')

names(crab_hel) <- c('SpCode', 'crab size', 'pri.key', 'sec_key',  'sea otter density', 'shoot density',  
                       'shoot density untransformed', 'seagrass biomass')
```


#Corrgram for independent variables
```{r}
#correlations
corrgram(crab_dun[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")

#correlations
corrgram(crab_gra[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")

#correlations
corrgram(crab_red[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")

#correlations
corrgram(crab_hel[,c(2, 5, 6, 8)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         cex.labels = 5,
         main="")
```

#VIF correlation check 
```{r}
dun1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_dun)
car::vif(dun1)

gra1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_gra)
car::vif(gra1)

red1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_red)
car::vif(red1)

hel1 <- lm(carapace_width_mm~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_hel)
car::vif(hel1)
```
