---
title: "crab_biomass_seagrass"
author: "Rebecca Cates"
date: "6/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load libraries
```{r warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(corrgram)
library(mgcv)
library(MASS)
library(pscl)
```

#Read in crab and shoot density data
```{r}
crab <- read.csv("crab_biomass.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) #eventually source from KNB

shoot <- read.csv("shoot_density.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) #eventually source from KNB

bio <- read.csv("seagrass_biomass.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA")) #eventually source from KNB
```

#Site level biomass
```{r}
crab <-
  crab %>% 
  group_by(sec_key, SpCode) %>% 
  dplyr::select(-c("trap", "mass.round", "string")) %>% 
  mutate(biomass = sum(mass)) %>% 
  dplyr::select(-c("mass")) %>% 
  distinct()
```

#Create effort column for bpue calculations
```{r}
crab$effort <- NA
crab$effort[crab$year == 17]  = 3
crab$effort[crab$year == 18]  = 4
crab$effort[crab$year == 19]  = 4
crab$effort[crab$year == 20]  = 3
```

#Clean up "shoot" df, calculate m2 shoot-density, and join with crab biomass and seagrass biomass df
#rename columns for clarity
```{r}
#Clean up shoot density df
shoot <-
  shoot %>% 
  rename(year = ï..year) %>% 
  mutate(shoot_m2 = shoot_dens*4)

#Clean up sg biomass df
bio <-
  bio %>% 
  dplyr::select(-c("X", "site_2019", "bay_code", "X.1", "X.2", "X.3"))

#Join dataframes
crab <- left_join(crab, shoot, by= "sec_key")
crab <- left_join(crab, bio, by= "sec_key")

#Clean up final df, select for needed columns
crab <-
  crab %>% 
  dplyr::select(-c("year.y", "bay_code", "shoot_dens", "shoot_dens_se")) %>% 
  rename(year = year.x, eg_mass_msq = avg_biom_msq, eg_shoot_msq = shoot_m2)


```

#Remove NAs from where there is no shoot density data
```{r}
crab <- crab[!is.na(crab$eg_mass_msq), ]
crab <- crab[!is.na(crab$eg_shoot_msq), ]
```

#Filter for species 
```{r}
crab_dun <-
  crab %>% 
  filter(SpCode %in% c("CRABDUN"))

crab_gra <-
  crab %>% 
  filter(SpCode %in% c("CRABGRA"))

crab_red <-
  crab %>% 
  filter(SpCode %in% c("CRABRR"))

crab_hel <-
  crab %>% 
  filter(SpCode %in% c("CRABHEL"))
```

#Filter for correct years for M. gracilis and C. magister
```{r}
crab_dun <-
  crab_dun %>% 
  filter(year %in% c("19", "20"))

crab_gra <-
  crab_gra %>% 
  filter(year %in% c("19", "20"))
```

#Create Biomass per unit effort column, bpue
```{r}
crab_dun$bpue <- NA
crab_dun$bpue <- (crab_dun$biomass/crab_dun$effort)

crab_gra$bpue <- NA
crab_gra$bpue <- (crab_gra$biomass/crab_gra$effort)

crab_red$bpue <- NA
crab_red$bpue <- (crab_red$biomass/crab_red$effort)

crab_hel$bpue <- NA
crab_hel$bpue <- (crab_hel$biomass/crab_hel$effort)

```

#Create rounded biomass column, bio_round
```{r}
crab_dun$bio_round <- NA
crab_dun$bio_round <- round(crab_dun$biomass)

crab_gra$bio_round <- NA
crab_gra$bio_round <- round(crab_gra$biomass)

crab_red$bio_round <- NA
crab_red$bio_round <- round(crab_red$biomass)

crab_hel$bio_round <- NA
crab_hel$bio_round <- round(crab_hel$biomass)
```

#Corrgram for independent variables
```{r}
#correlations
corrgram(crab_dun[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_DUN data in PC2/PC1 Order")

#correlations
corrgram(crab_gra[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_GRA data in PC2/PC1 Order")

#correlations
corrgram(crab_red[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_RED data in PC2/PC1 Order")

#correlations
corrgram(crab_hel[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_HEL data in PC2/PC1 Order")
```

#VIF correlation check 
```{r}
dun1 <- lm(biomass~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_dun)
car::vif(dun1)

gra1 <- lm(biomass~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_gra)
car::vif(gra1)

red1 <- lm(biomass~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_red)
car::vif(red1)

hel1 <- lm(biomass~otter_density+eg_shoot_msq+eg_mass_msq, data = crab_hel)
car::vif(hel1)
```

#Data visualization with untransformed data, crab mass ~ shoot density
```{r}
#C. magister==================================================
d <- ggplot(data = crab_dun, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression("A)"~paste(italic("C. magister,")~"data 2019-2020")))+
   theme(axis.title = element_blank(), text = element_text(size=15))
#M. gracilis =====================================================
g <- ggplot(data = crab_gra, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression(~"B)"~paste(italic("M. gracilis,")~"data 2019-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
#C. productus=====================================================
r <- ggplot(data = crab_red, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression(~"C)"~paste(italic("C. productus,")~"data 2017-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
#T. cheiragonus======================================================
h <- ggplot(data = crab_hel, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression(~"D)"~paste(italic("T. cheiragonus,")~"data 2017-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))

d
g
r
h
#arrange all plots 
mass <- gridExtra::grid.arrange(d, g, r, h,  ncol=2, nrow = 2)

annotate_figure(mass, bottom = text_grob(expression(Shoot~density~(no.~m^-2)), size = 20),left = text_grob(expression(Crab~biomass~(biomass.~site^-1)), rot=90, size = 20))
```

#Data visualization with sqrt data, crab mass ~ shoot density
```{r}
#C. magister==================================================
ggplot(data = crab_dun, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
 geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass(g)", title=expression(paste(italic("C. magister"))))+
  theme(text = element_text(size=15))
#M. gracilis =====================================================
ggplot(data = crab_gra, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("M. gracilis"))))+
  theme(text = element_text(size=15))
#C. productus=====================================================
ggplot(data = crab_red, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("C. productus"))))+
  theme(text = element_text(size=15))
#T. cheiragonus======================================================
ggplot(data = crab_hel, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("T. cheiragonus"))))+
  theme(text = element_text(size=15))
```

#Data visualization with untransformed data, crab mass ~ sg mass
```{r}
#C. magister==================================================
d <- ggplot(data = crab_dun, aes(x = eg_mass_msq, y= bio_round))+
  geom_point() +
  theme_light()+
 geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)), y= "Crab biomass (g)", title=expression("A)"~paste(italic("C. magister,")~"data 2019-2020")))+
  theme(axis.title = element_blank(), text = element_text(size=15))
#M. gracilis =====================================================
g <- ggplot(data = crab_gra, aes(x = eg_mass_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)),  y= "Crab biomass (g)", title=expression(~"B)"~paste(italic("M. gracilis,")~"data 2019-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
#C. productus=====================================================
r <- ggplot(data = crab_red, aes(x = eg_mass_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)),  y= "Crab biomass (g)", title=expression(~"C)"~paste(italic("C. productus,")~"data 2017-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
#T. cheiragonus======================================================
h <- ggplot(data = crab_hel, aes(x = eg_mass_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Seagrass~biomass~(g.~m^-2)),  y= "Crab biomass (g)", title=expression(~"D)"~paste(italic("T. cheiragonus,")~"data 2017-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))

d
g
r
h

#arrange all plots 
mass <- gridExtra::grid.arrange(d, g, r, h,  ncol=2, nrow = 2)

annotate_figure(mass, bottom = text_grob(expression(Seagrass~biomass~(g.~m^-2)), size = 20),left = text_grob(expression(Crab~biomass~(biomass.~site^-1)), rot=90, size = 20))
```

#Data analysis
#C. magister
```{r}
#Run GLMs
dun1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_dun)
summary(dun1)

dun2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_dun)
summary(dun2)

dun3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_dun)
summary(dun3)

dun4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_dun)
summary(dun4)

dun5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_dun)
summary(dun5)

dun6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_dun)
summary(dun6)

dun7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_dun)
summary(dun7)

dun8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_dun)
summary(dun8)

dun9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq+ log(offset(effort)), data = crab_dun)
summary(dun9)

dun10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_dun)
summary(dun10)

#Create list of models
dun_models <- list(dun1,dun2,dun3,dun4,dun5,dun6,dun7,dun8,dun9,dun10)
names(dun_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(dun1);AICc(dun2);AICc(dun3);AICc(dun4);AICc(dun5);AICc(dun6);AICc(dun7);AICc(dun8);AICc(dun9);AICc(dun10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(dun_models, modnames = names(dun_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#M. gracilis
```{r}
#Run zero inflated GLMs
gra1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra1)

gra2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra2)

gra3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_gra)
summary(gra3)

gra4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra4)

gra5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_gra)
summary(gra5)

gra6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_gra)
summary(gra6)

gra7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra7)

gra8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_gra)
summary(gra8)

gra9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq+ log(offset(effort)), data = crab_gra)
summary(gra9)

gra10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra10)

#Create list of models
gra_models <- list(gra1,gra2,gra3,gra4,gra5,gra6,gra7,gra8,gra9,gra10)
names(gra_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(gra1);AICc(gra2);AICc(gra3);AICc(gra4);AICc(gra5);AICc(gra6);AICc(gra7);AICc(gra8);AICc(gra9);AICc(gra10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(gra_models, modnames = names(gra_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#C. productus
```{r}
#Run zero inflated GLMs
red1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red1)

red2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red2)

red3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_red)
summary(red3)

red4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red4)

red5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_red)
summary(red5)

red6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_red)
summary(red6)

red7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red7)

red8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_red)
summary(red8)

red9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq+ log(offset(effort)), data = crab_red)
summary(red9)

red10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red10)

#Create list of models
red_models <- list(red1,red2,red3,red4,red5,red6,red7,red8,red9,red10)
names(red_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(red1);AICc(red2);AICc(red3);AICc(red4);AICc(red5);AICc(red6);AICc(red7);AICc(red8);AICc(red9);AICc(red10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(red_models, modnames = names(red_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#T. cheiragonus
```{r}
#Run zero inflated GLMs
hel1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel1)

hel2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel2)

hel3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_hel)
summary(hel3)

hel4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel4)

hel5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_hel)
summary(hel5)

hel6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_hel)
summary(hel6)

hel7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel7)

hel8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_hel)
summary(hel8)

hel9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel9)

hel10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel10)

#Create list of models
hel_models <- list(hel1,hel2,hel3,hel4,hel5,hel6,hel7,hel8,hel10)
names(hel_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(hel1);AICc(hel2);AICc(hel3);AICc(hel4);AICc(hel5);AICc(hel6);AICc(hel7);AICc(hel8);AICc(hel9);AICc(hel10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(hel_models, modnames = names(hel_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

