---
title: "crab_biomass_seagrass"
author: "Rebecca Cates"
date: "6/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
This script is associated with the manuscript "Effect of Sea Otter (Enhydra lutris) Predation and Habitat Structure on Nearshore Crab Assemblages in Southeast Alaska" by Rebecca Cates, Wendel Raymond, Lia Domke, and Ginny Eckert. This manuscript has been adapted from R.Cates master's thesis at the University of Alaska Fairbanks College of Fisheries and Ocean Science and is associated with the large, interdisciplinary project "APECS".

Crab abundance data were collected along the western coastline of Prince of Wales island with sites ranging 93 km from the most southern site in Dunbar Inlet up to the most northern site in Naukati Bay. Data was collected July to August, 2017-2020. Four strings with 2 pots each were were set at 21 different eelgrass sites. Pots soaked for ~24 hours before being pulled up to identify, measure and sex the contents of the pot. Abundance data was transformed to cpue and bpue data based on pot effort.

In addition, sea otter density data and seagrass biometric data was collected at these same sites from July through August, 2017-2020. Sea otters were counted via boat based surveys 2 nautical miles around the seagrass sites. Multiple individuals with binoculars were stationed at all angles from a 22' dual engine North River as the boat proceeded at a max speed of 8 knots. Sea otters were noted on the app "INAVX" with waypoints. Density per site was calculated in the script "Sea_otter_impact_index".Seagrass shoot density data was collected in 2017, 2018, and 2020 with eight 0.5-m × 0.5-m quadrats were evenly spaced every 12 m along a 100-m transect placed approximately -0.5 m relative to MLLW (Raymond et al. 2021). Eelgrass shoots were counted in each quadrat. Shoot density was then averaged across the eight quadrats per site. At each site in 2019, five 0.5-m x 0.5-m quadrats were randomly placed roughly 5-m linear distance below the upper edge of the eelgrass bed at all sites. Eelgrass shoots were counted in each quadrat and averaged.

Goal of this script :
1) Check for errors in data
2) Check for accuracy of data type and fix if needed (e.g., factor, numeric, character)
3) Analyze crab biomass, sea otter, and habitat data for all species
4) Visualize data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load libraries
```{r warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(MASS)
library(pscl)
library(visreg)
library(corrgram)
library(corrplot)
library(ggcorrplot)
library(MuMIn)
library(AICcmodavg)
library(ggbreak)
library(grid)
```

#Read in crab and shoot density data
```{r}
crab <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/Crab_Biomass_Seagrass/crab_biomass.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))

shoot <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/Crab_Abundance_Seagrass/shoot_density.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))
```

#Site level biomass
```{r}
crab <-
  crab %>% 
  group_by(sec_key, SpCode) %>% 
  dplyr::select(-c("trap", "mass.round", "string")) %>% 
  mutate(biomass = sum(mass)) %>% 
  dplyr::select(-c("mass")) %>% 
  distinct()
```

#Create effort column analysis
```{r}
crab$effort <- NA
crab$effort[crab$year == 2017]  = 3
crab$effort[crab$year == 2018]  = 4
crab$effort[crab$year == 2019]  = 4
crab$effort[crab$year == 2020]  = 3
```

#Calculate m2 shoot-density, and join with crab biomass df
```{r}
#Clean up shoot density df
shoot <-
  shoot %>% 
  mutate(shoot_m2 = shoot_dens*4)

#Join dataframes
crab <- left_join(crab, shoot, by= "sec_key")

#Clean up final df, select for needed columns
crab <-
  crab %>% 
  dplyr::select(-c("year.y", "bay_code", "shoot_dens", "shoot_dens_se")) %>% 
  rename(year = year.x, eg_shoot_msq = shoot_m2)


```

#Remove NAs from where there is no shoot density data
```{r}
crab <- crab[!is.na(crab$eg_shoot_msq), ]
```

#Filter for species 
```{r}
crab_dun <-
  crab %>% 
  filter(SpCode %in% c("CRABDUN"))

crab_gra <-
  crab %>% 
  filter(SpCode %in% c("CRABGRA"))

crab_red <-
  crab %>% 
  filter(SpCode %in% c("CRABRR"))

crab_hel <-
  crab %>% 
  filter(SpCode %in% c("CRABHEL"))
```

#Filter for correct years for M. gracilis and C. magister
```{r}
crab_dun <-
  crab_dun %>% 
  filter(year %in% c("2019", "2020"))

crab_gra <-
  crab_gra %>% 
  filter(year %in% c("2019", "2020"))
```

#Create Biomass per unit effort column, bpue
```{r}
crab_dun$bpue <- NA
crab_dun$bpue <- (crab_dun$biomass/crab_dun$effort)

crab_gra$bpue <- NA
crab_gra$bpue <- (crab_gra$biomass/crab_gra$effort)

crab_red$bpue <- NA
crab_red$bpue <- (crab_red$biomass/crab_red$effort)

crab_hel$bpue <- NA
crab_hel$bpue <- (crab_hel$biomass/crab_hel$effort)

```

#Create rounded biomass column, bio_round
```{r}
crab_dun$bio_round <- NA
crab_dun$bio_round <- round(crab_dun$biomass)

crab_gra$bio_round <- NA
crab_gra$bio_round <- round(crab_gra$biomass)

crab_red$bio_round <- NA
crab_red$bio_round <- round(crab_red$biomass)

crab_hel$bio_round <- NA
crab_hel$bio_round <- round(crab_hel$biomass)
```

#Year to factor, biomass to integer
```{r}
crab_dun <-
  crab_dun %>% 
  mutate_at(vars(year), 
            list(factor))
crab_dun$bio_round <- as.integer(crab_dun$bio_round)

crab_gra <-
  crab_gra %>% 
  mutate_at(vars(year), 
            list(factor))
crab_gra$bio_round <- as.integer(crab_gra$bio_round)

crab_red <-
  crab_red %>% 
  mutate_at(vars(year), 
            list(factor))
crab_red$bio_round <- as.integer(crab_red$bio_round)

crab_hel <-
  crab_hel %>% 
  mutate_at(vars(year), 
            list(factor))
crab_hel$bio_round <- as.integer(crab_hel$bio_round)


str(crab_dun)
```

#Corrgram for independent variables
```{r}
#correlations
corrgram(crab_dun[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_DUN data in PC2/PC1 Order")

#correlations
corrgram(crab_gra[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_GRA data in PC2/PC1 Order")

#correlations
corrgram(crab_red[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_RED data in PC2/PC1 Order")

#correlations
corrgram(crab_hel[,c(1,4:7)], 
         lower.panel=panel.shade,
         upper.panel=panel.cor,
         diag.panel= panel.density,
         main="CRAB_HEL data in PC2/PC1 Order")
```

#VIF correlation check 
```{r}
dun1 <- lm(biomass~otter_density+eg_shoot_msq, data = crab_dun)
car::vif(dun1)

gra1 <- lm(biomass~otter_density+eg_shoot_msq, data = crab_gra)
car::vif(gra1)

red1 <- lm(biomass~otter_density+eg_shoot_msq, data = crab_red)
car::vif(red1)

hel1 <- lm(biomass~otter_density+eg_shoot_msq, data = crab_hel)
car::vif(hel1)
```

#Data visualization with untransformed data, crab mass ~ shoot density
```{r}
#C. magister==================================================
d <- ggplot(data = crab_dun, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression("A)"~paste(italic("C. magister,")~"data 2019-2020")))+
   theme(axis.title = element_blank(), text = element_text(size=15))
d
#M. gracilis =====================================================
g <- ggplot(data = crab_gra, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression(~"B)"~paste(italic("M. gracilis,")~"data 2019-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
g
#C. productus=====================================================
r <- ggplot(data = crab_red, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression(~"C)"~paste(italic("C. productus,")~"data 2017-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
r
#T. cheiragonus======================================================
h <- ggplot(data = crab_hel, aes(x = eg_shoot_msq, y= bio_round))+
  geom_point() +
  theme_light()+
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= expression(Shoot~density~(no.~m^-2)), y= "Crab biomass (g)", title=expression(~"D)"~paste(italic("T. cheiragonus,")~"data 2017-2020")))+
    theme(axis.title = element_blank(), text = element_text(size=15))
h

#arrange all plots 
mass <- gridExtra::grid.arrange(d, g, r, h,  ncol=2, nrow = 2)

annotate_figure(mass, bottom = text_grob(expression(Shoot~density~(no.~m^-2)), size = 20),left = text_grob(expression(Crab~biomass~(biomass.~site^-1)), rot=90, size = 20))
```

#Data visualization with sqrt data, crab mass ~ shoot density
```{r}
#C. magister==================================================
ggplot(data = crab_dun, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
 geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass(g)", title=expression(paste(italic("C. magister"))))+
  theme(text = element_text(size=15))
#M. gracilis =====================================================
ggplot(data = crab_gra, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("M. gracilis"))))+
  theme(text = element_text(size=15))
#C. productus=====================================================
ggplot(data = crab_red, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("C. productus"))))+
  theme(text = element_text(size=15))
#T. cheiragonus======================================================
ggplot(data = crab_hel, aes(x = sqrt(eg_shoot_msq), y= sqrt(bio_round)))+
  geom_point() +
  geom_smooth(method = "glm.nb", formula = y~x)+
  labs(x= "Shoot Density", y= "Biomass", title=expression(paste(italic("T. cheiragonus"))))+
  theme(text = element_text(size=15))
```

#Data analysis
#C. magister
```{r}
#Run GLMs
dun1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + year, log(offset(effort)), data = crab_dun)
summary(dun1)

dun2 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_dun)
summary(dun2)

dun3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_dun)
summary(dun3)

dun4 <- glm.nb(bio_round ~ eg_shoot_msq + year, log(offset(effort)), data = crab_dun)
summary(dun4)

dun5 <- glm.nb(bio_round ~ otter_density, log(offset(effort)), data = crab_dun)
summary(dun5)

dun6 <- glm.nb(bio_round ~ eg_shoot_msq, log(offset(effort)), data = crab_dun)
summary(dun6)

dun7 <- glm.nb(bio_round ~  year, log(offset(effort)), data = crab_dun)
summary(dun7)

dun8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq, log(offset(effort)), data = crab_dun)
summary(dun8)

dun9 <- glm.nb(bio_round ~ otter_density*year, log(offset(effort)), data = crab_dun)
summary(dun9)

dun10 <- glm.nb(bio_round ~ eg_shoot_msq*year, log(offset(effort)), data = crab_dun)
summary(dun10)

#Create list of models
dun_models <- list(dun1,dun2,dun3,dun4,dun5,dun6,dun7,dun8,dun9,dun10)
names(dun_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(dun1);AICc(dun2);AICc(dun3);AICc(dun4);AICc(dun5);AICc(dun6);AICc(dun7);AICc(dun8);AICc(dun9);AICc(dun10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(dun_models, modnames = names(dun_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#M. gracilis
```{r}
#Run zero inflated GLMs
gra1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq  + log(offset(effort)), data = crab_gra)
summary(gra1)

gra2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra2)

gra3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_gra)
summary(gra3)

gra4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra4)

gra5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_gra)
summary(gra5)

gra6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_gra)
summary(gra6)

gra7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra7)

gra8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_gra)
summary(gra8)

gra9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq+ log(offset(effort)), data = crab_gra)
summary(gra9)

gra10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_gra)
summary(gra10)

#Create list of models
gra_models <- list(gra1,gra2,gra3,gra4,gra5,gra6,gra7,gra8,gra9,gra10)
names(gra_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(gra1);AICc(gra2);AICc(gra3);AICc(gra4);AICc(gra5);AICc(gra6);AICc(gra7);AICc(gra8);AICc(gra9);AICc(gra10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(gra_models, modnames = names(gra_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#C. productus
```{r}
#Run zero inflated GLMs
red1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red1)

red2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red2)

red3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_red)
summary(red3)

red4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red4)

red5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_red)
summary(red5)

red6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_red)
summary(red6)

red7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red7)

red8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_red)
summary(red8)

red9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq+ log(offset(effort)), data = crab_red)
summary(red9)

red10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_red)
summary(red10)

#Create list of models
red_models <- list(red1,red2,red3,red4,red5,red6,red7,red8,red9,red10)
names(red_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~sea otter density*seagrass biomass", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(red1);AICc(red2);AICc(red3);AICc(red4);AICc(red5);AICc(red6);AICc(red7);AICc(red8);AICc(red9);AICc(red10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(red_models, modnames = names(red_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

#T. cheiragonus
```{r}
#Run zero inflated GLMs
hel1 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel1)

hel2 <- glm.nb(bio_round ~ otter_density  + eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel2)

hel3 <- glm.nb(bio_round ~ otter_density + eg_shoot_msq + log(offset(effort)), data = crab_hel)
summary(hel3)

hel4 <- glm.nb(bio_round ~ eg_shoot_msq + eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel4)

hel5 <- glm.nb(bio_round ~ otter_density + log(offset(effort)), data = crab_hel)
summary(hel5)

hel6 <- glm.nb(bio_round ~ eg_shoot_msq + log(offset(effort)), data = crab_hel)
summary(hel6)

hel7 <- glm.nb(bio_round ~ eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel7)

hel8 <- glm.nb(bio_round ~ otter_density*eg_shoot_msq + log(offset(effort)), data = crab_hel)
summary(hel8)

hel9 <- glm.nb(bio_round ~ otter_density*eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel9)

hel10 <- glm.nb(bio_round ~ eg_shoot_msq*eg_mass_msq + log(offset(effort)), data = crab_hel)
summary(hel10)

#Create list of models
hel_models <- list(hel1,hel2,hel3,hel4,hel5,hel6,hel7,hel8,hel10)
names(hel_models) <- c("~sea otter density + shoot density + seagrass biomass", "~sea otter_density + seagrass biomass", "~sea otter density + shoot density", "~shoot density + seagrass biomass", "~sea otter density", "~shoot density", "~seagrass biomass", "~sea otter density*shoot density", "~shoot density*seagrass biomass" )
#Calculate AICc
library(MuMIn)
AICc(hel1);AICc(hel2);AICc(hel3);AICc(hel4);AICc(hel5);AICc(hel6);AICc(hel7);AICc(hel8);AICc(hel9);AICc(hel10)
#Calculate delta-AIC, and AIC weights
library(AICcmodavg)
aictab(hel_models, modnames = names(hel_models),
second.ord = TRUE, nobs = NULL, sort = TRUE)
```

