---
title: "CRAB_size"
author: "Becca Cates"
date: "1/14/2021"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This script is associated with the manuscript "Effect of Sea Otter (Enhydra lutris) Predation and Habitat Structure on Nearshore Crab Assemblages in Southeast Alaska" by Rebecca Cates, Wendel Raymond, Lia Domke, and Ginny Eckert. This manuscript has been adapted from R.Cates master's thesis at the University of Alaska Fairbanks College of Fisheries and Ocean Science and is associated with the large, interdisciplinary project "APECS".

Crab size data were collected along the western coastline of Prince of Wales island with sites ranging 93 km from the most southern site in Dunbar Inlet up to the most northern site in Naukati Bay. Data was collected July to August, 2017-2020. Four strings with 2 pots each were were set at 21 different eelgrass sites. Pots soaked for ~24 hours before being pulled up to identify, measure and sex the contents of the pot. 

In addition, sea otter density data was collected at these same sites from July through August, 2017-2020. Sea otters were counted via boat based surveys 2 nautical miles around the eelgrass sites. Multiple individuals with binoculars were stationed at all angles from a 22' dual engine North River as the boat proceeded at a max speed of 8 knots. Sea otters were noted on the app "INAVX" with waypoints. Density per site was calculated in the script "Sea_otter_impact_index".

Goal of this script :
1) Check for errors in data
2) Check for accuracy of data type and fix if needed (e.g., factor, numeric, character)
3) Analyze crab size distribution data for all species
4) Visualize data


#Load packages
```{r warning=FALSE}
library(tidyr)
library(datasets)
library(tidyverse)
library(dplyr)
library(MASS)
library(stats)
library(visreg)
library(coefplot)
library(ggplot2)
library(sandwich)
library(corrgram)
library(ggpubr)
library(AICcmodavg)
library(geiger)
library(ggpubr)
library(viridis)
library(car)
```

#Read in data
```{r}
#Crab size data
crab_size <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/clean_crab_otter_size_data_all_years.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))

#Sea otter density data
otter <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/Otter_density_site_allyears.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))

```

#Check for data errors
```{r}
#match sec_key of both data frames for join later on
summary(crab_size)
unique(crab_size$sec_key)

#looks good

```

#Filter otter df for columns and rows we need
```{r}
otter <- 
  otter %>% 
  dplyr::select(sec_key, avg.density)

crab_size<-
  crab_size %>% 
  dplyr::select(-c(otter_density))


```

#Join otter and crab dataframes by sec_key
```{r}
#Join otter and crab data
crab <- left_join(crab_size, otter, by= "sec_key")
#rename otter density column for clarity
crab <- 
 crab %>% 
  rename(otter_density = avg.density)
```

#create sea otter presence column
```{r}
crab$so_presence <- NA
crab$so_presence[crab$otter_density == 0] <- "Absent"
crab$so_presence[crab$otter_density != 0] <- "Present"

#convert to factor
crab$so_presence <- as.factor(crab$so_presence)
```

#Create year column
```{r}
#year based off of sec_key identifier
crab$year<- NA
crab$year[1:120] <- 2020
crab$year[121:381] <- 2017
crab$year[382:490] <- 2018
crab$year[491:754] <- 2019

crab$year <- as.factor(crab$year)
```

# Filter for species from df
# Filter out 2017, 2018 data due to size discrepency, for C.magister and C.gracilis
# Filter out 2018, 2019 data for T. Cheiragonus because no crabs were caught at sites without sea otters, cant do a comparison
```{r}
crab_dun<-
  crab%>% 
  filter(pri.key %in% c("CRABDUN.19", "CRABDUN.20"))

crab_gra<-
  crab %>% 
  filter(pri.key %in% c("CRABGRA.19", "CRABGRA.20"))

crab_red <-
  crab %>% 
  filter(pri.key %in% c("CRABRR.17", "CRABRR.18", "CRABRR.19", "CRABRR.20"))

crab_hel <-
  crab %>% 
  filter(pri.key %in% c("CRABHEL.17", "CRABHEL.20"))

```

#Density plots by species, carapace width density ~ sea otter presence
#With female and male crab size at maturity lines (used for R. Cates defense)
```{r}

#CRABDUN Density plot with sea otter presence
dun <- ggplot(data = crab_dun, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), 0.7))+
  geom_vline(aes(xintercept=174),
            color="#042333ff", linetype="dashed", linewidth=1)+
  geom_vline(aes(xintercept=95.13333),
            color="#f9a242ff", linetype="dashed", linewidth=1)+
   geom_vline(aes(xintercept=112),
            color="blue", linewidth=2)+
  geom_vline(aes(xintercept=106),
            color="red", linewidth=2)+
  # geom_vline(aes(xintercept=112),
   #         color="blue", linetype="solid", size=1)+ #size at maturity males
  # geom_vline(aes(xintercept=106),
   #         color="red", linetype="solid", size=1)+ #size at maturity females
  labs(title=expression("A)"),
         fill= "Sea Otter Presence")+
    theme(legend.position = "none")+
  xlim(25,190)+
  theme(text = element_text(size=20), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=75, y=0.06, label="Present\nMean = 95.1\nn=15", color="black", size=3, show.legend = FALSE)+ #mean line
  geom_label(fill="white", x=147, y=0.06, label="Absent\nMean = 174.0\nn=3", color="black", size=3, show.legend = FALSE) #mean line
  #geom_text(x=35, y=0.084, label="Data: 2019-2020", color="black", size=4, show.legend = FALSE) #data from years

#get legend
#legend <-get_legend(dun)
#remove legend from dun plot
#dun <- dun + theme(legend.position="none")

#view plot
dun

#CRABGRA Density plot with sea otter presence
gra <- ggplot(data = crab_gra, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), .7))+
  geom_vline(aes(xintercept=83.22034),
            color="#042333ff", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=65.47027),
            color="#f9a242ff", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=77),
            color="blue", size=2)+
  geom_vline(aes(xintercept=48),
            color="red", size=2)+
  #   geom_vline(aes(xintercept=77),
    #        color="blue", linetype="solid", size=1)+ #size at maturity males
   #geom_vline(aes(xintercept=48),
     #       color="red", linetype="solid", size=1)+ #size at maturity females
  labs(title=expression("B)"),
         fill= "Sea Otter Presence")+
  xlim(25,120)+
  theme(legend.position = "none")+
  theme(text = element_text(size=20), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=53, y=0.037, label="Present\nMean = 65.5\nn=186", color="black", size=3)+ #mean line
  geom_label(fill="white", x=101, y=0.037, label="Absent\nMean = 83.2\nn=59", color="black", size=3) #mean line
  geom_text(x=30.5, y=0.0455, label="Data: 2019-2020", color="black", size=4) #data from years

#view plot
gra

#CRABRED Density plot with sea otter presence
red <- ggplot(data = crab_red, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), .7))+
  geom_vline(aes(xintercept=129.0167),
            color="#042333ff", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=115.8017),
            color="#f9a242ff", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=65),
            color="blue", size=2)+
  geom_vline(aes(xintercept=64),
            color="red", size=2)+
 # geom_vline(aes(xintercept=65),
  #          color="Black", linetype="solid", size=1)+ ###size at maturity males and females
  labs(title=expression("C)"),
         fill= "Sea Otter Presence")+
  xlim(15,210)+
  theme(legend.position = "none")+
  theme(text = element_text(size=20), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=70, y=0.012, label="Present\nMean = 115.8\nn=122", color="black", size=3)+ #mean line
  geom_label(fill="white", x=182, y=0.012, label="Absent\nMean = 129.0\nn=120", color="black", size=3) #mean line
  geom_text(x=27, y=0.0148, label="Data: 2017-2020", color="black", size=4) #data from years

#view plot
red

#CRABHEL Density plot with sea otter presence
hel <- ggplot(data = crab_hel, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), 0.7))+
  geom_vline(aes(xintercept=39.66667),
            color="#042333ff", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=52.5),
            color="#f9a242ff", linetype="dashed", size=1)+
  geom_vline(aes(xintercept=34),
            color="blue", size=2)+
  geom_vline(aes(xintercept=36),
            color="red", size=2)+
 #    geom_vline(aes(xintercept=34),
  #          color="blue", linetype="solid", size=1)+ #size at maturity males
   #geom_vline(aes(xintercept=36),
    #        color="red", linetype="solid", size=1)+ #size at maturity females
  labs(title =expression("D)"),
         fill= "Sea Otter Presence")+
  xlim(-1,100)+
  theme(legend.position = "none")+
  theme(text = element_text(size=20), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=25, y=0.03, label="Absent\nMean = 39.7\nn=3", color="black", size=3)+ #mean line
  geom_label(fill="white", x=68, y=0.03, label="Present\nMean = 52.5\nn=82", color="black", size=3) #mean line
  geom_text(x=5, y=0.036, label="data: 2017-2020", color="black", size=4) #data from years
 
#view plot 
hel

#arrange all plots with legend (pulled from dun figure) at top
size <- gridExtra::grid.arrange(dun, gra, red, hel,  ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,4)),
             widths = c(2.7, 2.7), heights = c(2.5, 2.5))

annotate_figure(size, bottom = text_grob("Crab Carapace Width (mm)", size = 20),
                left = text_grob("Density", rot=90, size = 20))

#Annotated indvidual species figures
#C. magister
annotate_figure(dun, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
#M. gracilis
annotate_figure(gra, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
#C. productus
annotate_figure(red, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
#T. cheiragonus
annotate_figure(hel, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))

```

#Density plots by species, carapace width density ~ sea otter presence
#same chunk of code as above but no female and male crab size at maturity lines
```{r}

#CRABDUN Density plot with sea otter presence
dun <- ggplot(data = crab_dun, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), 0.7))+
  geom_vline(aes(xintercept=174),
            color="#042333ff", linetype="dashed", size=2)+
  geom_vline(aes(xintercept=95.13333),
            color="#f9a242ff", linetype="dashed", size=2)+
  # geom_vline(aes(xintercept=112),
   #         color="blue", linetype="solid", size=1)+ #size at maturity males
  # geom_vline(aes(xintercept=106),
   #         color="red", linetype="solid", size=1)+ #size at maturity females
  labs(title=expression("A)"),
         fill= "Sea Otter Presence")+
    theme(legend.position = "none")+
  xlim(25,190)+
  theme(text = element_text(size=15), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=70, y=0.06, label="Present\nMean = 95.1\nn=15", color="black", size=5, show.legend = FALSE)+ #mean line
  geom_label(fill="white", x=142, y=0.06, label="Absent\nMean = 174.0\nn=3", color="black", size=5, show.legend = FALSE) #mean line
  #geom_text(x=35, y=0.084, label="Data: 2019-2020", color="black", size=4, show.legend = FALSE) #data from years

#get legend
#legend <-get_legend(dun)
#remove legend from dun plot
#dun <- dun + theme(legend.position="none")

#CRABGRA Density plot with sea otter presence
gra <- ggplot(data = crab_gra, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), .7))+
  geom_vline(aes(xintercept=83.22034),
            color="#042333ff", linetype="dashed", size=2)+
  geom_vline(aes(xintercept=65.47027),
            color="#f9a242ff", linetype="dashed", size=2)+
  #   geom_vline(aes(xintercept=77),
    #        color="blue", linetype="solid", size=1)+ #size at maturity males
   #geom_vline(aes(xintercept=48),
     #       color="red", linetype="solid", size=1)+ #size at maturity females
  labs(title=expression("B)"),
         fill= "Sea Otter Presence")+
  xlim(25,120)+
  theme(legend.position = "none")+
  theme(text = element_text(size=15), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=48, y=0.037, label="Present\nMean = 65.5\nn=186", color="black", size=5)+ #mean line
  geom_label(fill="white", x=106, y=0.037, label="Absent\nMean = 83.2\nn=59", color="black", size=5) #mean line
  geom_text(x=30.5, y=0.0455, label="Data: 2019-2020", color="black", size=4) #data from years

#CRABRED Density plot with sea otter presence
red <- ggplot(data = crab_red, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), .7))+
  geom_vline(aes(xintercept=129.0167),
            color="#042333ff", linetype="dashed", size=2)+
  geom_vline(aes(xintercept=115.8017),
            color="#f9a242ff", linetype="dashed", size=2)+
 # geom_vline(aes(xintercept=65),
  #          color="Black", linetype="solid", size=1)+ ###size at maturity males and females
  labs(title=expression("C)"),
         fill= "Sea Otter Presence")+
  xlim(15,210)+
  theme(legend.position = "none")+
  theme(text = element_text(size=15), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=65, y=0.012, label="Present\nMean = 115.8\nn=122", color="black", size=5)+ #mean line
  geom_label(fill="white", x=187, y=0.012, label="Absent\nMean = 129.0\nn=120", color="black", size=5) #mean line
  geom_text(x=27, y=0.0148, label="Data: 2017-2020", color="black", size=4) #data from years

#CRABHEL Density plot with sea otter presence
hel <- ggplot(data = crab_hel, aes(x = carapace_width_mm, fill = so_presence))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), 0.7))+
  geom_vline(aes(xintercept=36.67),
            color="#042333ff", linetype="dashed", size=2)+
  geom_vline(aes(xintercept=52.5),
            color="#f9a242ff", linetype="dashed", size=2)+
 #    geom_vline(aes(xintercept=34),
  #          color="blue", linetype="solid", size=1)+ #size at maturity males
   #geom_vline(aes(xintercept=36),
    #        color="red", linetype="solid", size=1)+ #size at maturity females
  labs(title =expression("D)"),
         fill= "Sea Otter Presence")+
  xlim(-1,100)+
  theme(legend.position = "none")+
  theme(text = element_text(size=15), axis.title.y=element_blank(), axis.title.x=element_blank())+
  geom_label(fill="white", x=20, y=0.03, label="Absent\nMean = 36.67\nn=3", color="black", size=5)+ #mean line
  geom_label(fill="white", x=80, y=0.03, label="Present\nMean = 52.5\nn=82", color="black", size=5) #mean line
  geom_text(x=5, y=0.036, label="data: 2017-2020", color="black", size=4) #data from years
  

#arrange all plots with legend(pulled from dun figure) at top
size <- gridExtra::grid.arrange(dun, gra, red, hel,  ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,4)),
             widths = c(2.7, 2.7), heights = c(2.5, 2.5))

annotate_figure(size, bottom = text_grob("Crab Carapace Width (mm)", size = 18),
                left = text_grob("Density", rot=90, size = 18))

#Indvidual Species Figures
#C. magister
annotate_figure(dun, bottom = text_grob("Crab Carapace Width (mm)", size = 25),
                left = text_grob("Density", rot=90, size = 25))
#M. gracilis
annotate_figure(gra, bottom = text_grob("Crab Carapace Width (mm)", size = 25),
                left = text_grob("Density", rot=90, size = 25))
#C. productus
annotate_figure(red, bottom = text_grob("Crab Carapace Width (mm)", size = 25),
                left = text_grob("Density", rot=90, size = 25))
#T. cheiragonus
annotate_figure(hel, bottom = text_grob("Crab Carapace Width (mm)", size = 25),
                left = text_grob("Density", rot=90, size = 25))

```

#Carapace width~density figure stats
```{r}
#C. magister mean
mean(crab_dun$carapace_width_mm[crab_dun$so_presence == "Absent"]) #174
mean(crab_dun$carapace_width_mm[crab_dun$so_presence == "Present"]) #95.13333
table(crab_dun$so_presence) #absent=3, present = 15

#C. gracilis mean
mean(crab_gra$carapace_width_mm[crab_gra$so_presence == "Absent"]) #83.22034
mean(crab_gra$carapace_width_mm[crab_gra$so_presence == "Present"], na.rm=TRUE) #65.47027
table(crab_gra$so_presence) #absent=59, present = 186

#C. productus mean
mean(crab_red$carapace_width_mm[crab_red$so_presence == "Absent"]) #129.0167
mean(crab_red$carapace_width_mm[crab_red$so_presence == "Present"], na.rm=TRUE) #115.8017
table(crab_red$so_presence) #absent=120, present = 122

#T. cheiragonus mean
mean(crab_hel$carapace_width_mm[crab_hel$so_presence == "Absent"]) #39.67
mean(crab_hel$carapace_width_mm[crab_hel$so_presence == "Present"]) #52.5
table(crab_hel$so_presence) #absent=3, present = 52
```

#Two way ANOVA stats and Tukey Kramer post hoc
```{r}

#Shapiro Wilk
shapiro.test(crab_dun$carapace_width_mm)
shapiro.test(crab_gra$carapace_width_mm)
shapiro.test(crab_red$carapace_width_mm)
shapiro.test(crab_hel$carapace_width_mm)

#Levene's
leveneTest(carapace_width_mm ~ so_presence*year, data = crab_dun)
leveneTest(carapace_width_mm ~ so_presence*year, data = crab_gra)
leveneTest(carapace_width_mm ~ so_presence*year, data = crab_red)
leveneTest(carapace_width_mm ~ so_presence*year, data = crab_hel)

#Two way ANOVA, unbalanced design, type three sums of squares
anova_dun <- aov(carapace_width_mm~so_presence*year, data=crab_dun)
Anova(anova_dun, type = "III")

anova_gra <- aov(carapace_width_mm~so_presence*year, data=crab_gra)
Anova(anova_gra, type = "III")

anova_red <- aov(carapace_width_mm~so_presence*year, data=crab_red)
Anova(anova_red, type = "III")

anova_hel <- aov(carapace_width_mm~so_presence*year, data=crab_hel)
Anova(anova_hel, type = "III", singular.ok=TRUE)

#Tukey Kramer post hoc
print(TukeyHSD(anova_dun))
print(TukeyHSD(anova_gra))
print(TukeyHSD(anova_red))
print(TukeyHSD(anova_hel))
```

#Kruskal-Wallis test for so presence and mann-whitney test for year
```{r}
#wilcox
wilcox.test(carapace_width_mm ~ so_presence, data = crab_dun)
wilcox.test(carapace_width_mm ~ year, data = crab_dun)

wilcox.test(carapace_width_mm ~ so_presence, data = crab_gra)
wilcox.test(carapace_width_mm ~ year, data = crab_gra)

wilcox.test(carapace_width_mm ~ so_presence, data = crab_red)

wilcox.test(carapace_width_mm ~ so_presence, data = crab_hel)

#Kruskal with 
kruskal.test(carapace_width_mm ~ year, data = crab_dun)
pairwise.wilcox.test(crab_dun$carapace_width_mm, crab_dun$year,
                 p.adjust.method = "BH")

kruskal.test(carapace_width_mm ~ year, data = crab_gra)
pairwise.wilcox.test(crab_gra$carapace_width_mm, crab_gra$year,
                 p.adjust.method = "BH")

kruskal.test(carapace_width_mm ~ year, data = crab_red)
pairwise.wilcox.test(crab_red$carapace_width_mm, crab_red$year,
                 p.adjust.method = "BH")

kruskal.test(carapace_width_mm ~ year, data = crab_hel)
pairwise.wilcox.test(crab_hel$carapace_width_mm, crab_hel$year,
                 p.adjust.method = "BH")
```

#Density plots by species, carapace width density ~ year
```{r}
#CRABDUN Density plot with year
dun <- ggplot(data = crab_dun, aes(x = carapace_width_mm, fill = year))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), .7))+
  geom_vline(aes(xintercept=106.625),
            color="#042333ff", linetype="dashed", size=2)+
    geom_vline(aes(xintercept=121.5),
            color="#f9a242ff", linetype="dashed", size=2)+
  labs(title=expression("A)"),
         fill= "Year")+
  xlim(25,190)+
   theme(legend.position = "none",text = element_text(size=15),
        axis.title.y=element_blank(), axis.title.x=element_blank())+
   geom_label(fill="white", x=47, y=0.012, label="Mean\n2019 = 106.6, n = 16\n2020 = 121.5, n = 2", color="black", size=5) #mean line

dun <- dun + theme(legend.position="none")

#CRABGRA Density plot with year
gra <- ggplot(data = crab_gra, aes(x = carapace_width_mm, fill = year))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#042333ff", "#f9a242ff"), .7))+
  geom_vline(aes(xintercept=72.19886),
            color="#042333ff", linetype="dashed", size=2)+
    geom_vline(aes(xintercept=63.45),
            color="#f9a242ff", linetype="dashed", size=2)+
  labs(title=expression("B)"),
         fill= "Year")+
  xlim(25,120)+
  theme(legend.position = "none",text = element_text(size=15),
        axis.title.y=element_blank(), axis.title.x=element_blank())+
    geom_label(fill="white", x=37, y=0.029, label="Mean\n2019 = 72.2, n = 177\n2020 = 63.5, n = 68", color="black", size=5) #mean line

gra <- gra + theme(legend.position="none")


#CRABRED Density plot with year
red <- ggplot(data = crab_red, aes(x = carapace_width_mm, fill = year))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#238A8DFF", "#55C667FF","#042333ff", "#f9a242ff"), .7))+
    geom_vline(aes(xintercept=115.8614),
            color="#238A8DFF", linetype="dashed", size=2)+
    geom_vline(aes(xintercept=140.6923),
            color="#55C667FF", linetype="dashed", size=2)+
  geom_vline(aes(xintercept=116.8571),
            color="#042333ff", linetype="dashed", size=2)+
    geom_vline(aes(xintercept=122.875),
            color="#f9a242ff", linetype="dashed", size=2)+
    labs(title=expression("C)"),
         fill= "Year")+
  xlim(15,210)+
  theme(legend.position = "none",text = element_text(size=15),
        axis.title.y=element_blank(), axis.title.x=element_blank())+
    geom_label(fill="white", x=42, y=0.021, label="Mean\n2017 = 116.0, n = 103\n2018 = 140.7, n = 52\n2019 = 116.9, n = 57\n2020 = 122.9, n = 32", color="black", size=5) #mean line

#get legend
legend <-get_legend(red)
#remove legend from red plot
red <- red + theme(legend.position="none")


#CRABHEL Density plot with sea otter presence
hel <- ggplot(data = crab_hel, aes(x = carapace_width_mm, fill = year))+
  geom_density() +
  theme_classic()+
  scale_fill_manual(values = alpha(c("#238A8DFF", "#55C667FF","#042333ff", "#f9a242ff"), .7))+
   geom_vline(aes(xintercept=48.27027),
            color= "#238A8DFF", linetype="dashed", size=2)+
  geom_vline(aes(xintercept=58.6),
            color= "#55C667FF", linetype="dashed", size=2)+
    labs(title=expression("D)"),
         fill= "Year")+
  xlim(-1,100)+
  theme(legend.position = "none",text = element_text(size=15),
        axis.title.y=element_blank(), axis.title.x=element_blank())+
    geom_label(fill="white", x=11, y=0.040, label="Mean\n2017 = 48.3, n = 37\n2020 = 58.6, n = 18 ", color="black", size=5)

#arrange all plots with legend(pulled from dun figure) at top
size <- gridExtra::grid.arrange(dun, gra, red, hel,  ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,4)),
             widths = c(2.7, 2.7), heights = c(2.5, 2.5))

size2 <- annotate_figure(size, bottom = text_grob("Crab Carapace Width (mm)", size = 18),left = text_grob("Density", rot=90, size = 18))


size2

#Indvidual Species Figures
#C. magister
dun <- gridExtra::grid.arrange(legend, dun,  ncol=1, nrow = 2,
                               widths = c(2.7), heights = c(0.3, 2.5))
annotate_figure(dun, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
#M. gracilis
gra <- gridExtra::grid.arrange(legend, gra,  ncol=1, nrow = 2,
                               widths = c(2.7), heights = c(0.3, 2.5))
annotate_figure(gra, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
#C. productus
red <- gridExtra::grid.arrange(legend, red,  ncol=1, nrow = 2,
                               widths = c(2.7), heights = c(0.3, 2.5))
annotate_figure(red, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
#T. cheiragonus
hel <- gridExtra::grid.arrange(legend, hel,  ncol=1, nrow = 2,
                               widths = c(2.7), heights = c(0.3, 2.5))
annotate_figure(hel, bottom = text_grob("Crab Carapace Width (mm)", size = 15),
                left = text_grob("Density", rot=90, size = 15))
```

#Figure stats
```{r}
#Dungeness crab mean
mean(crab_dun$carapace_width_mm[crab_dun$year == "2019"]) #106.625
mean(crab_dun$carapace_width_mm[crab_dun$year == "2020"]) #121.5
table(crab_dun$year) #2019=16, 2020 = 2

#slender rock crab mean
mean(crab_gra$carapace_width_mm[crab_gra$year == "2019"], na.rm=TRUE) #72.19886
mean(crab_gra$carapace_width_mm[crab_gra$year == "2020"], na.rm=TRUE) #63.45588
table(crab_gra$year) #2019=177, 2020 = 68

#red rock crab mean
mean(crab_red$carapace_width_mm[crab_red$year == "2017"]) #115.8614
mean(crab_red$carapace_width_mm[crab_red$year == "2018"], na.rm=TRUE) #140.6923
mean(crab_red$carapace_width_mm[crab_red$year == "2019"], na.rm=TRUE) #116.8571
mean(crab_red$carapace_width_mm[crab_red$year == "2020"], na.rm=TRUE) #122.875
table(crab_red$year) #2017=101, 2018=52, 2019=57, 2020=32

#helmet crab mean
mean(crab_hel$carapace_width_mm[crab_hel$year == "2017"]) #48.27027
mean(crab_hel$carapace_width_mm[crab_hel$year == "2018"]) #44.875
mean(crab_hel$carapace_width_mm[crab_hel$year == "2019"]) #61.78571
mean(crab_hel$carapace_width_mm[crab_hel$year == "2020"]) #58.61111
table(crab_hel$year) #2017=37, 2018=16, 2019=14, 2020=18


```

#Interaction Plots by species
```{r}
facet_dun = ggplot(crab_dun, aes(x= so_presence, y=carapace_width_mm, fill = so_presence)) + 
  geom_boxplot(alpha = 1) + 
  theme_classic()+
  facet_grid(~year)+
  theme(legend.position = "none",text = element_text(size=15),  axis.title.y=element_blank(), axis.title.x=element_blank())+
   labs(x="Sea Otter Presence",
        y= "Crab Carapace Width (mm)",
        title =expression("A)"))+
  scale_fill_brewer(palette="Paired")
 
facet_dun

facet_gra = ggplot(crab_gra, aes(x= so_presence, y=carapace_width_mm, fill = so_presence)) +
  geom_boxplot() + 
  theme_classic()+
  facet_grid(~year)+
 theme(legend.position = "none",text = element_text(size=15),  axis.title.y=element_blank(), axis.title.x=element_blank())+
   labs(x="Sea Otter Presence",
        y= "Crab Carapace Width (mm)",
        title =expression("B)"))+
    scale_fill_brewer(palette="Paired")

 
facet_gra

facet_red = ggplot(crab_red, aes(x= so_presence, y=carapace_width_mm, fill = so_presence)) +
  geom_boxplot() + 
  theme_classic()+
  facet_grid(~year)+
  theme(legend.position = "none",text = element_text(size=15),  axis.title.y=element_blank(), axis.title.x=element_blank())+
   labs(x="Sea Otter Presence",
        y= "Crab Carapace Width (mm)",
        title =expression("C)"))+
    scale_fill_brewer(palette="Paired")

 
facet_red

facet_hel = ggplot(crab_hel,aes(x= so_presence, y=carapace_width_mm, fill = so_presence)) +
  geom_boxplot() + 
  theme_classic()+
  facet_grid(~year)+
 theme(legend.position = "none",text = element_text(size=15),  axis.title.y=element_blank(), axis.title.x=element_blank())+
   labs(x="Sea Otter Presence",
        y= "Crab Carapace Width (mm)",
        title =expression("D)"))+
    scale_fill_brewer(palette="Paired")

 
facet_hel

facet <- gridExtra::grid.arrange(facet_dun, facet_gra, facet_red, facet_hel,  ncol=1, nrow = 4)

facet2 <- annotate_figure(facet, bottom = text_grob("Sea otter presence", size = 15),left = text_grob("Crab carapace width(mm)", rot=90, size = 15))

facet2
```

