---
title: "crab_catch_analysis"
author: "Rebecca Cates"
date: "6/8/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load packages
```{r warning=FALSE}
library(dplyr)
library(tidyr)
library(segmented)
library(SiZer)
library(ggplot2)
library(ggpubr)
library(MASS)
library(cowplot)
```

#Read in crab data
```{r}
crab_cpue <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/crab_BPUE.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))

crab_bpue <- read.csv("https://raw.githubusercontent.com/catesbecca/cates_crab_manuscript/main/Data%26Scripts/crab_BPUE.csv", header = TRUE, stringsAsFactors = FALSE, na.strings=c("","NA"))
```

#Filter by species for CPUE data analysis
```{r}
crab_dun <-
  crab_cpue %>% 
  filter(SpCode %in% c("CRABDUN"))

crab_gra <-
  crab_cpue %>% 
  filter(SpCode %in% c("CRABGRA"))

crab_red <-
  crab_cpue %>% 
  filter(SpCode %in% c("CRABRED"))

crab_hel <-
  crab_cpue %>% 
  filter(SpCode %in% c("CRABHEL"))
```

#Segmented Regression with package "SiZer and untransformed data
#using qplot to plot segments at breakpoint (knot)
```{r}
#C. magister=================================================
#Save and run bootstrap segmented regression
dun <- 
  piecewise.linear(crab_dun$otter_density, crab_dun$cpue,
                   middle = 1,
                   CI = TRUE,
                   bootstrap.samples = 1000,
                   sig.level = 0.05)
#View results
dun
str(dun)
dun$model
dun$CI

#Save figure
d.cpue <- 
  qplot(otter_density, cpue, geom =
          c('point','smooth'), method = 'lm', se = F, data = crab_dun) +
  theme_classic()+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "A)")+
  ylim(0,5)
#View figure
d.cpue
#C. gracilis=========================================================
#Save and run bootstrap segmented regression
gra <- piecewise.linear(crab_gra$otter_density,
                        crab_gra$cpue,
                        middle = 1,
                        CI = TRUE,
                        bootstrap.samples = 1000,
                        sig.level = 0.05)
#View results
gra
#Save figure
g.cpue <- 
  qplot(otter_density, cpue, geom = c('point', 'smooth'), method = 'lm', se = F, data = crab_gra) +
  theme_classic()+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "B)")+
  ylim(0,30)
#View figure
g.cpue

summary(g)
g$coordinates
#C. productus==========================================
#Save and run bootstrap segmented regression
red <- 
  piecewise.linear(crab_red$otter_density, crab_red$cpue,
                   middle = 0,
                   CI = TRUE,
                   bootstrap.samples = 1000,
                   sig.level = 0.05)
#View results
red
#Save figure
r.cpue <- 
  qplot(otter_density, cpue, group = otter_density >  1.62, geom = 
          c('point', 'smooth'), method = 'lm', se = F, data = crab_red) +
  theme_classic()+
  annotate("rect", xmin = 0.07, xmax = 2.90, ymin = 0, ymax = 40,
        alpha = .2)+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "C)")+
  geom_vline(xintercept = 1.62, linetype = "dashed", size=1.2, color= "black") +
  ylim(0,10)

#View figure
r.cpue

#T. cheiragonus====================================================
#Run and save bootstrap segmented regression
hel <- 
  piecewise.linear(crab_hel$otter_density,crab_hel$cpue,
                   middle = 1,
                   CI = TRUE,
                   bootstrap.samples = 1000,
                   sig.level = 0.05)
#View results
hel
#Save figure
h.cpue <- 
  qplot(otter_density, cpue, group = otter_density > 10.12, geom = 
          c('point', 'smooth'), method = 'lm', se = F, data = crab_hel) +
  theme_classic()+
  annotate("rect", xmin = 6, xmax = 19.60, ymin = 0, ymax = 40,
        alpha = .2)+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "D)")+
  geom_vline(xintercept = 10, linetype = "dashed", size=1.2, color= "black") +
  ylim(0,10)

#View figure
h.cpue

#arrange all plots 
crab_cpue <- gridExtra::grid.arrange(d.cpue, g.cpue, r.cpue, h.cpue,  ncol=2, nrow = 2)

annotate_figure(catch, top = text_grob("CPUE Breakpoint Estimates", size=20), bottom = text_grob(expression(Sea~otter~density~(ind.~km^-2)), size = 20),left = text_grob(expression(CPUE), rot=90, size = 20))
```


#DID NOT USE FOR THESIS
#Segmented regression using "segmented" function
#Instead of sizer, "segmented" requires that you manually look at the data and estimate a range where the breakpoint occurs
#Other option: Do not provide estimates and use "psi=NA"
```{r}
#C. magister=================================================
#Create a linear model
dun.lm <- lm(cpue ~ otter_density, data = crab_dun)
summary(dun.lm)

#Visualize data to estimate breakpoint range
ggplot(data = crab_dun, aes(x = otter_density, y= cpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "CPUE", title=expression(paste(italic("C. magister"))))+
  theme(text = element_text(size=15))

#Run segmented regression on linear model providing estimates
dun.seg <- segmented(dun.lm)

#View results
summary(dun.seg)
#Get the breakpoints
dun.seg$psi
#get the slopes
slope(dun.seg)
# get the fitted data
dun.fitted <- fitted(dun.seg)
dun.model <- data.frame(Density = crab_dun$otter_density, cpue = dun.fitted)

# plot the fitted model
d <- ggplot(dun.model, aes(x =Density, y = cpue)) + 
  geom_point() +
  geom_line() +
  geom_line(data = dun.model, aes(x = Density, y = cpue), colour = "tomato")
dun.lines <- dun.seg$psi[, 2]

d <- d + geom_vline(xintercept = dun.lines, linetype = "dashed")
d
#run F-test to test lm vs bp model
dun_aov <- anova(dun.lm, dun.seg)
dun_aov

#C. gracilis=================================================
#Create a linear model
gra.lm <- lm(cpue ~ otter_density, data = crab_gra)
summary(gra.lm)

#Visualize data to estimate break point range
ggplot(data = crab_gra, aes(x = otter_density, y= cpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "cpue", title=expression(paste(italic("M. gracilis"))))+
  theme(text = element_text(size=15))

#Run segmented regression on linear model providing estimates
gra.seg <- segmented(gra.lm)
#View results
summary(gra.seg)
#Get the breakpoints
gra.seg$psi
#get the slopes
slope(gra.seg)
# get the fitted data
gra.fitted <- fitted(gra.seg)
gra.model <- data.frame(Density = crab_gra$otter_density, cpue = gra.fitted)

# plot the fitted model
g <- ggplot(gra.model, aes(x =Density, y = cpue)) + 
  geom_point() +
  geom_line() +
  geom_line(data = gra.model, aes(x = Density, y = cpue), colour = "tomato")
gra.lines <- gra.seg$psi[, 2]

g <- g + geom_vline(xintercept = gra.lines, linetype = "dashed")
g
#run F-test to test lm vs bp model
anova(gra.lm, gra.seg)

#C. productus=================================================
#Create a linear model
red.lm <- lm(cpue ~ otter_density, data = crab_red)
summary(red.lm)

#Visualize data to esimate breakpoint range
ggplot(data = crab_red, aes(x = otter_density, y= cpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "cpue", title=expression(paste(italic("C. productus"))))+
  theme(text = element_text(size=15))
#breakpoint range appears to be between 0 and 5

#Run segmented regression on linear model providing estimates
red.seg <- segmented(red.lm)

#View results
summary(red.seg)
#Get the breakpoints
red.seg$psi
#get the slopes
slope(red.seg)
# get the fitted data
red.fitted <- fitted(red.seg)
red.model <- data.frame(Density = crab_red$otter_density, cpue = red.fitted)

# plot the fitted model
r <- ggplot(red.model, aes(x =Density, y = cpue)) + 
  geom_point() +
  geom_line() +
  geom_line(data = red.model, aes(x = Density, y = cpue), colour = "tomato")
red.lines <- red.seg$psi[, 2]

r <- r + geom_vline(xintercept = red.lines, linetype = "dashed")
r
#run F-test to test lm vs bp model
anova(red.lm, red.seg)

#T. cheiragonus=================================================
#Create a linear model
hel.lm <- lm(cpue ~ otter_density, data = crab_hel)
summary(hel.lm)

#Visualize data to esimate breakpoint range
ggplot(data = crab_hel, aes(x = otter_density, y= cpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "cpue", title=expression(paste(italic("T. cheiragonus"))))+
  theme(text = element_text(size=15))
#breakpoint range appears to be between 3 and 8

#Run segmented regression on linear model providing estimates
hel.seg <- segmented(hel.lm)
#View results
summary(hel.seg)
#Get the breakpoints
hel.seg$psi
#get the slopes
slope(hel.seg)
# get the fitted data
hel.fitted <- fitted(hel.seg)
hel.model <- data.frame(Density = crab_hel$otter_density, cpue = hel.fitted)

# plot the fitted model
h <- ggplot(hel.model, aes(x =Density, y = cpue)) + 
  geom_point() +
  geom_line() +
  geom_line(data = hel.model, aes(x = Density, y = cpue), colour = "tomato")
hel.lines <- hel.seg$psi[, 2]

h <- h + geom_vline(xintercept = hel.lines, linetype = "dashed")
h
#run F-test to test lm vs bp model
anova(hel.lm, hel.seg)
```

#BREAK IN SCRIPT
#We are switching from CPUE calculations to BPUE calculation

#Filter for species 
```{r}
crab_dun <-
  crab_bpue %>% 
  filter(SpCode %in% c("CRABDUN"))

crab_gra <-
  crab_bpue %>% 
  filter(SpCode %in% c("CRABGRA"))

crab_red <-
  crab_bpue %>% 
  filter(SpCode %in% c("CRABRR"))

crab_hel <-
  crab_bpue %>% 
  filter(SpCode %in% c("CRABHEL"))
```

#Segmented Regression with package "SiZer and untransformed data
#using qplot to plot segments at breakpoint (knot)
```{r}
#C. magister=================================================
#Save and run bootstrap segmented regression
dun <- 
  piecewise.linear(crab_dun$otter_density, crab_dun$bpue,
                   middle = 1,
                   CI = TRUE,
                   bootstrap.samples = 1000,
                   sig.level = 0.05)
#View results
dun
str(dun)
dun$model
dun$CI

#Save figure
d.bpue <- 
  qplot(otter_density, bpue, group = otter_density > 0.27, geom =
          c('point','smooth'), method = 'lm', se = F, data = crab_dun) +
  theme_classic()+
  annotate("rect", xmin = 0.03, xmax = 16, ymin = 0, ymax = 1500,
        alpha = .2)+
  labs(title = "E)")+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  geom_vline(xintercept = 0.27, linetype = "dashed", size=1.2, color= "black")+
  ylim(0,150)
#View figure
d.bpue

#M. gracilis=========================================================
#Save and run bootstrap segmented regression
gra <- piecewise.linear(crab_gra$otter_density,
                        crab_gra$bpue,
                        middle = 1,
                        CI = TRUE,
                        bootstrap.samples = 1000,
                        sig.level = 0.05)
#View results
gra
#Save figure
g.bpue <- 
  qplot(otter_density, bpue, geom = c('point', 'smooth'), method = 'lm', se = F, data = crab_gra) +
  theme_classic()+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "F)")+
  ylim(0,1000)
#View figure
g.bpue

#C. productus==========================================
#Save and run bootstrap segmented regression
red <- 
  piecewise.linear(crab_red$otter_density, crab_red$bpue,
                   middle = 0,
                   CI = TRUE,
                   bootstrap.samples = 1000,
                   sig.level = 0.05)
#View results
red
#Save figure
r.bpue <- 
  qplot(otter_density, bpue, group = otter_density >  1.48, geom = 
          c('point', 'smooth'), method = 'lm', se = F, data = crab_red) +
  theme_classic()+
 # annotate("rect", xmin = 0.06, xmax = 2.81, ymin = 0, ymax = 1500,
       # alpha = .2)+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "G)")+
  geom_vline(xintercept = 1.549, linetype = "dashed", size=1.2, color= "black") +
  ylim(0,1500)

#View figure
r.bpue

#T. cheiragonus====================================================
#Run and save bootstrap segmented regression
hel <- 
  piecewise.linear(crab_hel$otter_density,crab_hel$bpue,
                   middle = 1,
                   CI = TRUE,
                   bootstrap.samples = 1000,
                   sig.level = 0.05)
#View results
print(hel)
#Save figure
h.bpue <- 
  qplot(otter_density, bpue, group = otter_density > 9.38, geom = 
          c('point', 'smooth'), method = 'lm', se = F, data = crab_hel) +
  theme_classic()+
  annotate("rect", xmin = 6.64, xmax = 17.24, ymin = 0, ymax = 1500,
        alpha = .2)+
  theme(axis.title = element_blank(), plot.title = element_text(size=15), axis.text = element_text(size=15))+
  labs(title = "H)")+
  geom_vline(xintercept = 8.623, linetype = "dashed", size=1.2, color= "black") +
  ylim(0,300)

#View figure
h.bpue
#arrange all plots 
crab_bpue <- gridExtra::grid.arrange(d.bpue, g.bpue, r.bpue, h.bpue,  ncol=2, nrow = 2)

annotate_figure(crab_bpue, bottom = text_grob(expression(Sea~otter~density~(ind.~km^-2)), size = 20),left = text_grob("Biomass (BPUE)", rot=90, size = 20))
```

#DID NOT USE FOR THESIS
#Segmented regression using "segmented" function
#Instead of sizer, "segmented" requires that you manually look at the data and estimate a range where the breakpoint occurs
#Can also not provide estimates and use "psi=NA"
```{r}
#C. magister=================================================
#Create a linear model
dun.lm <- lm(bpue ~ otter_density, data = crab_dun)
summary(dun.lm)

#Visualize data to estimate breakpoint range
ggplot(data = crab_dun, aes(x = otter_density, y= bpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "Biomass", title=expression(paste(italic("C. magister"))))+
  theme(text = element_text(size=15))
#breakpoint range appears to be between 3 and 8

#Run segmented regression on linear model providing estimates
dun.seg <- segmented(dun.lm)

#View results
summary(dun.seg)
#Get the breakpoints
dun.seg$psi
#get the slopes
slope(dun.seg)
# get the fitted data
dun.fitted <- fitted(dun.seg)
dun.model <- data.frame(Density = crab_dun$otter_density, Biomass = dun.fitted)

# plot the fitted model
d <- ggplot(dun.model, aes(x =Density, y = Biomass)) + 
  geom_point() +
  geom_line() +
  geom_line(data = dun.model, aes(x = Density, y = Biomass), colour = "tomato")
dun.lines <- dun.seg$psi[, 2]

d <- d + geom_vline(xintercept = dun.lines, linetype = "dashed")
d
#run F-test to test lm vs bp model
anova(dun.lm, dun.seg)
#M. gracilis=================================================
#Create a linear model
gra.lm <- lm(bpue ~ otter_density, data = crab_gra)
summary(gra.lm)

#Visualize data to esimate breakpoint range
ggplot(data = crab_gra, aes(x = otter_density, y= bpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "Biomass", title=expression(paste(italic("M. gracilis"))))+
  theme(text = element_text(size=15))
#breakpoint range appears to be between 5 and 15

#Run segmented regression on linear model providing estimates
gra.seg <- segmented(gra.lm)
#View results
summary(gra.seg)
#Get the breakpoints
gra.seg$psi
#get the slopes
slope(gra.seg)
# get the fitted data
gra.fitted <- fitted(gra.seg)
gra.model <- data.frame(Density = crab_gra$otter_density, Biomass = gra.fitted)

# plot the fitted model
g <- ggplot(gra.model, aes(x =Density, y = Biomass)) + 
  geom_point() +
  geom_line() +
  geom_line(data = gra.model, aes(x = Density, y = Biomass), colour = "tomato")
gra.lines <- gra.seg$psi[, 2]

g <- g + geom_vline(xintercept = gra.lines, linetype = "dashed")
g

crab_gra$second_seg <- pmax(0, crab_gra$otter_density-15.47)
crab_gra[1:43,]

# Fit the known change point model
second_fit <- lm(bpue ~ otter_density + second_seg, data=crab_gra)
summary(second_fit)

#run F-test to test lm vs bp model
anova(gra.lm, second_fit)
#C. productus=================================================
#Create a linear model
red.lm <- lm(bpue ~ otter_density, data = crab_red)
summary(red.lm)

#Visualize data to esimate breakpoint range
ggplot(data = crab_red, aes(x = otter_density, y= bpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "Biomass", title=expression(paste(italic("C. productus"))))+
  theme(text = element_text(size=15))
#breakpoint range appears to be between 0 and 5

#Run segmented regression on linear model providing estimates
red.seg <- segmented(red.lm)
#View results
summary(red.seg)
#Get the breakpoints
red.seg$psi
#get the slopes
slope(red.seg)
# get the fitted data
red.fitted <- fitted(red.seg)
red.model <- data.frame(Density = crab_red$otter_density, Biomass = red.fitted)

# plot the fitted model
r <- ggplot(red.model, aes(x =Density, y = Biomass)) + 
  geom_point() +
  geom_line() +
  geom_line(data = red.model, aes(x = Density, y = Biomass), colour = "tomato")
red.lines <- red.seg$psi[, 2]

r <- r + geom_vline(xintercept = red.lines, linetype = "dashed")
r
#run F-test to test lm vs bp model
anova(red.lm, red.seg)
#T. cheiragonus=================================================
#Create a linear model
hel.lm <- lm(bpue ~ otter_density, data = crab_hel)
summary(hel.lm)

#Visualize data to esimate breakpoint range
ggplot(data = crab_hel, aes(x = otter_density, y= bpue))+
  geom_point() +
  geom_smooth(method="lm")+
  labs(x= "Sea Otter Density", y= "Biomass", title=expression(paste(italic("T. cheiragonus"))))+
  theme(text = element_text(size=15))
#breakpoint range appears to be between 3 and 8

#Run segmented regression on linear model providing estimates
hel.seg <- segmented(hel.lm)
#View results
summary(hel.seg)
#Get the breakpoints
hel.seg$psi
#get the slopes
slope(hel.seg)
# get the fitted data
hel.fitted <- fitted(hel.seg)
hel.model <- data.frame(Density = crab_hel$otter_density, Biomass = hel.fitted)

# plot the fitted model
h <- ggplot(hel.model, aes(x =Density, y = Biomass)) + 
  geom_point() +
  geom_line() +
  geom_line(data = hel.model, aes(x = Density, y = Biomass), colour = "tomato")
hel.lines <- hel.seg$psi[, 2]

h <- h + geom_vline(xintercept = hel.lines, linetype = "dashed")
h
#run F-test to test lm vs bp model
anova(hel.lm, hel.seg)
```

#Arrange cpue and cpue plots together 
```{r}
crab_cpue <- gridExtra::grid.arrange(d.cpue, g.cpue, r.cpue, h.cpue, ncol=1, nrow = 4)
crab_cpue <- annotate_figure(catch, left = text_grob("Crab abundance (CPUE)", rot=90, size = 15))
crab_cpue

crab_bpue <- gridExtra::grid.arrange(d.bpue, g.bpue, r.bpue, h.bpue,  ncol=1, nrow = 4)
crab_bpue <- annotate_figure(mass, left = text_grob("Crab biomass (BPUE)", rot=90, size = 15))
crab_bpue

crab_cpue_bpue <-  gridExtra::grid.arrange(crab_cpue, crab_bpue,  ncol=2, nrow = 1)
annotate_figure(crab_cpue_bpue, bottom = text_grob(expression(Sea~otter~density~(ind.~km^-2)), size = 15), top = text_grob(expression(Crab~CPUE~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Crab~BPUE), size = 15))
```

